---
title: "Pilot 3: Graphs after removing outliers, using ReactionTime Column"
author: "morgan moyer"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
library(stringr)
library(textstem)
library(tidyverse)
theme_set(theme_bw())
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73")
this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../../../helpers.R")

d <- read.csv("../data/processed")
```

# Looking at overall Log ReactionTime for the data

Before removing outliers

## Summary Stats
```{r}

ggplot(d, aes(ReactionTime, fill=Task)) +
  geom_density(alpha = .5)

summary(d$ReactionTime)
```

Long tail justifies outlier removal?
```{r}
ggplot(d, aes(LogReactionTime, fill=Task)) +
  geom_density(alpha = .5)

summary(d$LogReactionTime)
```

# ReactionTime by CorrectedAccuracy

```{r}
agr = d %>%
    group_by(Task,LogReactionTime) %>%
    summarize(MeanCorrectedAccuracy = mean(CorrectedAccuracy) )


ggplot(agr, aes(x = MeanCorrectedAccuracy, y = LogReactionTime, fill = MeanCorrectedAccuracy)) +
  geom_boxplot(alpha = 0.7) + # Boxplot
  geom_jitter(position = position_jitter(0.2), color = "black", size = 1.5, alpha = 0.5) + # Add jittered points
  facet_wrap(~Task) +
  labs(title = "Reaction Time by CorrectedAccuracy",
       x = "CorrectedAccuracy",
       y = "Reaction Time (ms)") +
  
  theme(legend.position = "none") # Remove legend

```

```{r}
ggplot(d, aes(x = CorrectedAccuracy, y = LogReactionTime, fill = Task)) +
  geom_violin(alpha = 0.7) + # Violin plot
  geom_jitter(position = position_jitter(0.2), color = "black", size = 1.5, alpha = 0.5) + # Add jittered points
  labs(title = "Reaction Time by CorrectedAccuracy",
       x = "CorrectedAccuracy",
       y = "Reaction Time (ms)")
  
  # theme(legend.position = "none") # Remove legend
```

# CorrectedAccuracy


## Overall CorrectedAccuracy
```{r}
agr <- d %>% 
  group_by(Task) %>% 
  reframe(MeanCorrectedAccuracy = mean(CorrectedAccuracy), 
          CILow = ci.low(CorrectedAccuracy), 
          CIHigh = ci.high(CorrectedAccuracy)) %>%
  mutate(YMin = MeanCorrectedAccuracy - CILow, 
         YMax = MeanCorrectedAccuracy + CIHigh)
dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanCorrectedAccuracy,fill=Task)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))


```

## Mean CorrectedAccuracy by Word / Task
```{r,fig.width=10, fig.height=5}
agr <- d %>%
  group_by(Task,Word) %>% 
  mutate(MeanCorrectedAccuracy = mean(CorrectedAccuracy), 
          CILow = ci.low(CorrectedAccuracy), 
          CIHigh = ci.high(CorrectedAccuracy)) %>%
  mutate(YMin = MeanCorrectedAccuracy - CILow, 
         YMax = MeanCorrectedAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Word,y=MeanCorrectedAccuracy,fill=Task)) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")

```

## Mean CorrectedAccuracy by Word / Block Order

```{r,fig.width=10, fig.height=5}
agr <- d %>%
  group_by(BlockOrder,Word) %>% 
  mutate(MeanCorrectedAccuracy = mean(CorrectedAccuracy), 
          CILow = ci.low(CorrectedAccuracy), 
          CIHigh = ci.high(CorrectedAccuracy)) %>%
  mutate(YMin = MeanCorrectedAccuracy - CILow, 
         YMax = MeanCorrectedAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Word,y=MeanCorrectedAccuracy,fill=BlockOrder)) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")

```


## Mean CorrectedAccuracy by participant
```{r,fig.width=10, fig.height=5}
agr <- d %>%
  group_by(Task,ID.true) %>% 
  mutate(MeanCorrectedAccuracy = mean(CorrectedAccuracy), 
          CILow = ci.low(CorrectedAccuracy), 
          CIHigh = ci.high(CorrectedAccuracy)) %>%
  mutate(YMin = MeanCorrectedAccuracy - CILow, 
         YMax = MeanCorrectedAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=ID.true,y=MeanCorrectedAccuracy,fill=Task)) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```


# First Remove participants who aren't super , aggregating over Task

```{r}
length(unique(d$ID.true))
inacc.parts <- d %>% 
  group_by(ID.true) %>% 
  summarise(MeanCorrectedAccuracy = mean(CorrectedAccuracy)) %>% 
  filter(MeanCorrectedAccuracy < .75)

# How many participants have accuracy < .75?
length(unique(inacc.parts$ID.true))

d.inaccurate.removed <- d %>% 
  anti_join(inacc.parts, by = "ID.true")

# Sanity check
length(unique(d.inaccurate.removed$ID.true))

```

### Look at those graphs again

### Overall CorrectedAccuracy
```{r}
agr <- d.inaccurate.removed %>% 
  group_by(Task) %>% 
  reframe(MeanCorrectedAccuracy = mean(CorrectedAccuracy), 
          CILow = ci.low(CorrectedAccuracy), 
          CIHigh = ci.high(CorrectedAccuracy)) %>%
  mutate(YMin = MeanCorrectedAccuracy - CILow, 
         YMax = MeanCorrectedAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanCorrectedAccuracy,fill=Task)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))


```

### Mean CorrectedAccuracy by Word / Task
```{r,fig.width=10, fig.height=5}
agr <- d.inaccurate.removed %>%
  group_by(Task,Word) %>% 
  mutate(MeanCorrectedAccuracy = mean(CorrectedAccuracy), 
          CILow = ci.low(CorrectedAccuracy), 
          CIHigh = ci.high(CorrectedAccuracy)) %>%
  mutate(YMin = MeanCorrectedAccuracy - CILow, 
         YMax = MeanCorrectedAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Word,y=MeanCorrectedAccuracy,fill=Task)) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


### Mean CorrectedAccuracy by participant
```{r,fig.width=10, fig.height=10}
agr <- d.inaccurate.removed %>%
  group_by(Task,ID.true) %>% 
  mutate(MeanCorrectedAccuracy = mean(CorrectedAccuracy), 
          CILow = ci.low(CorrectedAccuracy), 
          CIHigh = ci.high(CorrectedAccuracy)) %>%
  mutate(YMin = MeanCorrectedAccuracy - CILow, 
         YMax = MeanCorrectedAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=ID.true,y=MeanCorrectedAccuracy,fill=Task)) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```



## Remove outliers
```{r}
# Remove subjects with ReactionTime higher than 3x IQR
summary(d.inaccurate.removed$LogReactionTime)
  #  Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  # 6.924   7.328   7.436   7.479   7.579  10.008 
range(d.inaccurate.removed$LogReactionTime)

hist(d.inaccurate.removed$LogReactionTime, breaks=100, col="lightblue", xlab="LogReactionTime (ms)",
        main="Histogram with Normal Curve")

quantile(d.inaccurate.removed$LogReactionTime)
IQR(d.inaccurate.removed$LogReactionTime)*3 # 0.7526289
cutoff.high <- quantile(d.inaccurate.removed$LogReactionTime)[4] + IQR(d.inaccurate.removed$LogReactionTime)*3 # 8.419261
cutoff.low <- quantile(d.inaccurate.removed$LogReactionTime)[2] - IQR(d.inaccurate.removed$LogReactionTime)*3# 6.5088838.419261


# remove subjects with ReactionTime higher than 3 x IQR
df.outliers.removed <- subset(d.inaccurate.removed, (d.inaccurate.removed$LogReactionTime > cutoff.low) & (d.inaccurate.removed$LogReactionTime < cutoff.high))

hist(df.outliers.removed$LogReactionTime, col="lightblue", xlab="LogReactionTime (ms)",
        main="Histogram with Normal Curve")

```


# ReactionTime by CorrectedAccuracy

```{r}
agr = df.outliers.removed %>%
    group_by(Task, LogReactionTime) %>%
    summarize(MeanCorrectedAccuracy = mean(CorrectedAccuracy))

ggplot(agr, aes(x = MeanCorrectedAccuracy, y = LogReactionTime, fill = MeanCorrectedAccuracy)) +
  geom_boxplot(alpha = 0.7) +  # Boxplot
  geom_jitter(position = position_jitter(0.2), color = "black", size = 1.5, alpha = 0.5) + # Add jittered points
  facet_wrap(~Task) +
  labs(title = "Reaction Time by CorrectedAccuracy",
       x = "CorrectedAccuracy",
       y = "Reaction Time (ms)") +
  theme(legend.position = "none")  # Remove legend

```

```{r}
ggplot(df.outliers.removed, aes(x = CorrectedAccuracy, y = LogReactionTime, fill = Task)) +
  geom_violin(alpha = 0.7) + # Violin plot
  geom_jitter(position = position_jitter(0.2), color = "black", size = 1.5, alpha = 0.5) + # Add jittered points 
  labs(title = "Reaction Time by CorrectedAccuracy",
       x = "CorrectedAccuracy",
       y = "Reaction Time (ms)")

```

# CorrectedAccuracy


## Overall CorrectedAccuracy
```{r}
agr <- df.outliers.removed %>% 
  group_by(Task) %>% 
  reframe(MeanCorrectedAccuracy = mean(CorrectedAccuracy), 
          CILow = ci.low(CorrectedAccuracy), 
          CIHigh = ci.high(CorrectedAccuracy)) %>%
  mutate(YMin = MeanCorrectedAccuracy - CILow, 
         YMax = MeanCorrectedAccuracy + CIHigh)
# View(agr)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanCorrectedAccuracy,fill=Task)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))

  # theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  # guides(fill = "none")

```

## Mean CorrectedAccuracy by Word / Task
```{r,fig.width=10, fig.height=5}
agr <- df.outliers.removed %>%
  # filter(PennElementType == "Selector") %>% 
  # select(ID.true,Word,CorrectedAccuracy) %>% 
  group_by(Task,Word) %>% 
  mutate(MeanCorrectedAccuracy = mean(CorrectedAccuracy), 
          CILow = ci.low(CorrectedAccuracy), 
          CIHigh = ci.high(CorrectedAccuracy)) %>%
  mutate(YMin = MeanCorrectedAccuracy - CILow, 
         YMax = MeanCorrectedAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Word,y=MeanCorrectedAccuracy,fill=Task)) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  guides(fill = "none")

# View(d[(d$ID.true == c("56cc78e3ccc0e20006b82a7d")) & (d$Word == c("envy")),])
```

## Mean CorrectedAccuracy by Word / Block Order

```{r,fig.width=10, fig.height=5}
agr <- df.outliers.removed %>%
  group_by(BlockOrder,Word) %>% 
  mutate(MeanCorrectedAccuracy = mean(CorrectedAccuracy), 
          CILow = ci.low(CorrectedAccuracy), 
          CIHigh = ci.high(CorrectedAccuracy)) %>%
  mutate(YMin = MeanCorrectedAccuracy - CILow, 
         YMax = MeanCorrectedAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Word,y=MeanCorrectedAccuracy,fill=BlockOrder)) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")

# View(d[(d$ID.true == c("56cc78e3ccc0e20006b82a7d")) & (d$Word == c("envy")),])
```





# ReactionTime by Task
```{r}

agr = df.outliers.removed %>%
    group_by(Task,Word) %>%
    summarize(MeanReactionTime = mean(ReactionTime), 
              CILow = ci.low(ReactionTime), 
              CIHigh = ci.high(ReactionTime)) %>%
    mutate(YMin = MeanReactionTime - CILow, 
           YMax = MeanReactionTime + CIHigh)

ggplot(agr, aes(x=MeanReactionTime, fill=Task)) +
  geom_density(alpha = .4)

ggplot(agr, aes(x=Task, y=MeanReactionTime,fill=Task)) + 
    geom_violin(trim=FALSE,alpha=.4) +
    geom_jitter(position = position_jitter(0.2), color = "black", size = 1.5, alpha = 0.5) + # Add jittered points
    guides(fill = "none")

```


# ReactionTime by BlockOrder and Task
```{r}

agr = df.outliers.removed %>%
    group_by(BlockOrder,Task,Word) %>%
    summarize(MeanReactionTime = mean(ReactionTime), 
              CILow = ci.low(ReactionTime), 
              CIHigh = ci.high(ReactionTime)) %>%
    mutate(YMin = MeanReactionTime - CILow, 
           YMax = MeanReactionTime + CIHigh)

ggplot(agr, aes(x=MeanReactionTime, fill=Task)) +
  geom_density(alpha = .4)

ggplot(agr, aes(x=MeanReactionTime, fill=Task)) +
  facet_wrap(~BlockOrder) +
  geom_density(alpha = .4)

ggplot(agr, aes(x=Task, y=MeanReactionTime,fill=BlockOrder)) + 
    geom_violin(trim=FALSE,alpha=.4) +
    geom_point(color = "black", size = 1.5, alpha = 0.5)  # Centered points

```


# By Item

```{r,fig.width=10, fig.height=5}
agr = df.outliers.removed %>%
    group_by(Task,Word) %>%
    summarize(MeanReactionTime = mean(ReactionTime), CILow = ci.low(ReactionTime), CIHigh = ci.high(ReactionTime)) %>%
    mutate(YMin = MeanReactionTime - CILow, YMax = MeanReactionTime + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Word,y=MeanReactionTime,fill=Task)) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")
```

```{r,fig.width=10, fig.height=15}
agr = df.outliers.removed %>%
    group_by(BlockOrder,Task,Word) %>%
    summarize(MeanReactionTime = mean(ReactionTime), CILow = ci.low(ReactionTime), CIHigh = ci.high(ReactionTime)) %>%
    mutate(YMin = MeanReactionTime - CILow, YMax = MeanReactionTime + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanReactionTime,fill=BlockOrder)) +
  geom_bar(position=dodge,stat="identity") +
  facet_wrap(~Word,ncol=5) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")
```


## By ConcValCombo category and Task

### Mean Raw ReactionTime and Effects of Word Valence/Concreteness

```{r}

agr = df.outliers.removed %>%
    group_by(Task,ConcValCombo) %>%
    reframe(MeanReactionTime = mean(ReactionTime), CILow = ci.low(ReactionTime), CIHigh = ci.high(ReactionTime)) %>%
    mutate(YMin = MeanReactionTime - CILow, YMax = MeanReactionTime + CIHigh)


dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanReactionTime,fill=ConcValCombo)) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")


```

### Mean Raw ReactionTime and Effects of Word Valence/Concreteness

```{r}

agr = df.outliers.removed %>%
    group_by(BlockOrder,Task,ConcValCombo) %>%
    reframe(MeanReactionTime = mean(ReactionTime), CILow = ci.low(ReactionTime), CIHigh = ci.high(ReactionTime)) %>%
    mutate(YMin = MeanReactionTime - CILow, YMax = MeanReactionTime + CIHigh)


dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanReactionTime,fill=BlockOrder)) +
  geom_bar(position=dodge,stat="identity") +
  facet_wrap(~ConcValCombo) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")


```






# Compare Remove participants who aren't super accuracy, grouping by Task

i actually don't think this is the right call if we want to look at within-subjects behavior

```{r}
inacc.parts.group <- d %>% 
  group_by(Task,ID.true) %>% 
  summarise(MeanCorrectedAccuracy = mean(CorrectedAccuracy)) %>% 
  filter(MeanCorrectedAccuracy < .75)

# How many participants have accuracy < .75?
length(unique(inacc.parts.group$ID.true))

d.inaccurate.removed.group <- d %>% 
  anti_join(inacc.parts.group, by = "ID.true")

# Sanity check
length(unique(d.inaccurate.removed.group$ID.true))

```

### Look at those graphs again

### Overall CorrectedAccuracy
```{r}
agr <- d.inaccurate.removed.group %>% 
  group_by(Task) %>% 
  reframe(MeanCorrectedAccuracy = mean(CorrectedAccuracy), 
          CILow = ci.low(CorrectedAccuracy), 
          CIHigh = ci.high(CorrectedAccuracy)) %>%
  mutate(YMin = MeanCorrectedAccuracy - CILow, 
         YMax = MeanCorrectedAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanCorrectedAccuracy,fill=Task)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))


```

### Mean CorrectedAccuracy by Word / Task
```{r,fig.width=10, fig.height=5}
agr <- d.inaccurate.removed.group %>%
  group_by(Task,Word) %>% 
  mutate(MeanCorrectedAccuracy = mean(CorrectedAccuracy), 
          CILow = ci.low(CorrectedAccuracy), 
          CIHigh = ci.high(CorrectedAccuracy)) %>%
  mutate(YMin = MeanCorrectedAccuracy - CILow, 
         YMax = MeanCorrectedAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Word,y=MeanCorrectedAccuracy,fill=Task)) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


### Mean CorrectedAccuracy by participant
```{r,fig.width=10, fig.height=10}
agr <- d.inaccurate.removed.group %>%
  group_by(Task,ID.true) %>% 
  mutate(MeanCorrectedAccuracy = mean(CorrectedAccuracy), 
          CILow = ci.low(CorrectedAccuracy), 
          CIHigh = ci.high(CorrectedAccuracy)) %>%
  mutate(YMin = MeanCorrectedAccuracy - CILow, 
         YMax = MeanCorrectedAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=ID.true,y=MeanCorrectedAccuracy,fill=Task)) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```



## Remove outliers for reacton time


```{r}
# Remove subjects with ReactionTime higher than 3x IQR
summary(d.inaccurate.removed.group$LogReactionTime)
  #  Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  # 6.924   7.328   7.436   7.479   7.579  10.008 
range(d.inaccurate.removed.group$LogReactionTime)

hist(d.inaccurate.removed.group$LogReactionTime, breaks=100, col="lightblue", xlab="LogReactionTime (ms)",
        main="Histogram with Normal Curve")

quantile(d.inaccurate.removed.group$LogReactionTime)
IQR(d.inaccurate.removed.group$LogReactionTime)*3 # 0.7526289
cutoff.high <- quantile(d.inaccurate.removed.group$LogReactionTime)[4] + IQR(d.inaccurate.removed.group$LogReactionTime)*3 # 8.419261
cutoff.low <- quantile(d.inaccurate.removed.group$LogReactionTime)[2] - IQR(d.inaccurate.removed.group$LogReactionTime)*3# 6.5088838.419261


# remove subjects with ReactionTime higher than 3 x IQR
df.outliers.removed.group <- subset(d.inaccurate.removed.group, (d.inaccurate.removed.group$LogReactionTime > cutoff.low) & (d.inaccurate.removed.group$LogReactionTime < cutoff.high))

hist(df.outliers.removed.group$LogReactionTime, col="lightblue", xlab="LogReactionTime (ms)",
        main="Histogram with Normal Curve")

```

# ReactionTime by CorrectedAccuracy

```{r}
agr = df.outliers.removed.group %>%
    group_by(Task,LogReactionTime) %>%
    summarize(MeanCorrectedAccuracy = mean(CorrectedAccuracy) )


ggplot(agr, aes(x = MeanCorrectedAccuracy, y = LogReactionTime, fill = MeanCorrectedAccuracy)) +
  geom_boxplot(alpha = 0.7) + # Boxplot
  geom_jitter(position = position_jitter(0.2), color = "black", size = 1.5, alpha = 0.5) + # Add jittered points
  facet_wrap(~Task) +
  labs(title = "Reaction Time by CorrectedAccuracy",
       x = "CorrectedAccuracy",
       y = "Reaction Time (ms)") +

  theme(legend.position = "none") # Remove legend

```

```{r}
ggplot(df.outliers.removed.group, aes(x = CorrectedAccuracy, y = LogReactionTime, fill = Task)) +
  geom_violin(alpha = 0.7) + # Violin plot
  geom_jitter(position = position_jitter(0.2), color = "black", size = 1.5, alpha = 0.5) + # Add jittered points
  labs(title = "Reaction Time by CorrectedAccuracy",
       x = "CorrectedAccuracy",
       y = "Reaction Time (ms)")
  
  # theme(legend.position = "none") # Remove legend
```

# CorrectedAccuracy


## Overall CorrectedAccuracy
```{r}
agr <- df.outliers.removed.group %>% 
  group_by(Task) %>% 
  reframe(MeanCorrectedAccuracy = mean(CorrectedAccuracy), 
          CILow = ci.low(CorrectedAccuracy), 
          CIHigh = ci.high(CorrectedAccuracy)) %>%
  mutate(YMin = MeanCorrectedAccuracy - CILow, 
         YMax = MeanCorrectedAccuracy + CIHigh)
# View(agr)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanCorrectedAccuracy,fill=Task)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))

  # theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  # guides(fill = "none")

```

## Mean CorrectedAccuracy by Word / Task
```{r,fig.width=10, fig.height=5}
agr <- df.outliers.removed.group %>%
  # filter(PennElementType == "Selector") %>% 
  # select(ID.true,Word,CorrectedAccuracy) %>% 
  group_by(Task,Word) %>% 
  mutate(MeanCorrectedAccuracy = mean(CorrectedAccuracy), 
          CILow = ci.low(CorrectedAccuracy), 
          CIHigh = ci.high(CorrectedAccuracy)) %>%
  mutate(YMin = MeanCorrectedAccuracy - CILow, 
         YMax = MeanCorrectedAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Word,y=MeanCorrectedAccuracy,fill=Task)) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  guides(fill = "none")

# View(d[(d$ID.true == c("56cc78e3ccc0e20006b82a7d")) & (d$Word == c("envy")),])
```

## Mean CorrectedAccuracy by Word / Block Order

```{r,fig.width=10, fig.height=5}
agr <- df.outliers.removed.group %>%
  group_by(BlockOrder,Word) %>% 
  mutate(MeanCorrectedAccuracy = mean(CorrectedAccuracy), 
          CILow = ci.low(CorrectedAccuracy), 
          CIHigh = ci.high(CorrectedAccuracy)) %>%
  mutate(YMin = MeanCorrectedAccuracy - CILow, 
         YMax = MeanCorrectedAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Word,y=MeanCorrectedAccuracy,fill=BlockOrder)) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")

# View(d[(d$ID.true == c("56cc78e3ccc0e20006b82a7d")) & (d$Word == c("envy")),])
```





# ReactionTime by Task
```{r}

agr = df.outliers.removed.group %>%
    group_by(Task,Word) %>%
    summarize(MeanReactionTime = mean(ReactionTime), 
              CILow = ci.low(ReactionTime), 
              CIHigh = ci.high(ReactionTime)) %>%
    mutate(YMin = MeanReactionTime - CILow, 
           YMax = MeanReactionTime + CIHigh)

ggplot(agr, aes(x=MeanReactionTime, fill=Task)) +
  geom_density(alpha = .4)

ggplot(agr, aes(x=Task, y=MeanReactionTime,fill=Task)) + 
    geom_violin(trim=FALSE,alpha=.4) +
    geom_point(color = "black", size = 1.5, alpha = 0.5)  # Centered points
```


# ReactionTime by BlockOrder and Task
```{r}

agr = df.outliers.removed.group %>%
    group_by(BlockOrder,Task,Word) %>%
    summarize(MeanReactionTime = mean(ReactionTime), 
              CILow = ci.low(ReactionTime), 
              CIHigh = ci.high(ReactionTime)) %>%
    mutate(YMin = MeanReactionTime - CILow, 
           YMax = MeanReactionTime + CIHigh)

ggplot(agr, aes(x=MeanReactionTime, fill=Task)) +
  geom_density(alpha = .4)

ggplot(agr, aes(x=MeanReactionTime, fill=Task)) +
  facet_wrap(~BlockOrder) +
  geom_density(alpha = .4)

ggplot(agr, aes(x=Task, y=MeanReactionTime,fill=BlockOrder)) + 
    geom_violin(trim=FALSE,alpha=.4) +
    geom_point(color = "black", size = 1.5, alpha = 0.5)

```


# By Item

```{r,fig.width=10, fig.height=5}
agr = df.outliers.removed.group %>%
    group_by(Task,Word) %>%
    summarize(MeanReactionTime = mean(ReactionTime), CILow = ci.low(ReactionTime), CIHigh = ci.high(ReactionTime)) %>%
    mutate(YMin = MeanReactionTime - CILow, YMax = MeanReactionTime + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Word,y=MeanReactionTime,fill=Task)) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")
```

```{r,fig.width=10, fig.height=15}
agr = df.outliers.removed.group %>%
    group_by(BlockOrder,Task,Word) %>%
    summarize(MeanReactionTime = mean(ReactionTime), CILow = ci.low(ReactionTime), CIHigh = ci.high(ReactionTime)) %>%
    mutate(YMin = MeanReactionTime - CILow, YMax = MeanReactionTime + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanReactionTime,fill=BlockOrder)) +
  geom_bar(position=dodge,stat="identity") +
  facet_wrap(~Word,ncol=5) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")
```


## By ConcValCombo category and Task

### Mean Raw ReactionTime and Effects of Word Valence/Concreteness

```{r}

agr = df.outliers.removed.group %>%
    group_by(Task,ConcValCombo) %>%
    reframe(MeanReactionTime = mean(ReactionTime), CILow = ci.low(ReactionTime), CIHigh = ci.high(ReactionTime)) %>%
    mutate(YMin = MeanReactionTime - CILow, YMax = MeanReactionTime + CIHigh)


dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanReactionTime,fill=ConcValCombo)) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))


```

### Mean Raw ReactionTime and Effects of Word Valence/Concreteness

```{r}

agr = df.outliers.removed.group %>%
    group_by(BlockOrder,Task,ConcValCombo) %>%
    reframe(MeanReactionTime = mean(ReactionTime), CILow = ci.low(ReactionTime), CIHigh = ci.high(ReactionTime)) %>%
    mutate(YMin = MeanReactionTime - CILow, YMax = MeanReactionTime + CIHigh)


dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanReactionTime,fill=BlockOrder)) +
  geom_bar(position=dodge,stat="identity") +
  facet_wrap(~ConcValCombo) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))


```
