---
title: "Pilot 4: Corrected Analysis without outliers: ReactionTime Column"
author: "morgan moyer"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
library(stringr)
library(textstem)
library(tidyverse)
theme_set(theme_bw())
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73")
this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../../../helpers.R")

d <- read.csv("../data/corrected.csv")
```



```{r}

ggplot(d, aes(x=LogReactionTime)) +
  geom_histogram(binwidth = .1,fill = "lightblue", color = "black") +
  facet_wrap(~Task)

ggplot(d, aes(x=LogReactionTime, fill=Task)) +
  geom_density(alpha = .4)

```

# First Remove participants who aren't super , aggregating over Task

```{r}
length(unique(d$ID.true))
inacc.parts <- d %>% 
  group_by(ID.true) %>% 
  summarise(MeanAccuracyCorrected = mean(AccuracyCorrected)) %>% 
  filter(MeanAccuracyCorrected < .75)

# How many participants have AccuracyCorrected < .75?
length(unique(inacc.parts$ID.true))

d.inaccurate.removed <- d %>% 
  anti_join(inacc.parts, by = "ID.true")

# Sanity check
length(unique(d.inaccurate.removed$ID.true))

```

# remove all inaccurate trials
```{r}
orig <- nrow(d.inaccurate.removed)
d.inaccurate.removed <- d.inaccurate.removed %>% 
  filter(AccuracyCorrected == 1)
nrow(d.inaccurate.removed)/orig*100

```



```{r}
# Remove subjects with ReactionTime higher than 3x IQR
summary(d.inaccurate.removed$LogReactionTime)
  #  Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  # 6.924   7.328   7.436   7.479   7.579  10.008 
range(d.inaccurate.removed$LogReactionTime)

hist(d.inaccurate.removed$LogReactionTime, breaks=100, col="lightblue", xlab="LogReactionTime (ms)",
        main="Histogram with Normal Curve")

quantile(d.inaccurate.removed$LogReactionTime)
IQR(d.inaccurate.removed$LogReactionTime)*3 # 0.7526289
cutoff.high <- quantile(d.inaccurate.removed$LogReactionTime)[4] + IQR(d.inaccurate.removed$LogReactionTime)*3 # 8.419261
cutoff.low <- quantile(d.inaccurate.removed$LogReactionTime)[2] - IQR(d.inaccurate.removed$LogReactionTime)*3# 6.5088838.419261


# remove subjects with ReactionTime higher than 3 x IQR
df.outliers.removed <- subset(d.inaccurate.removed, (d.inaccurate.removed$LogReactionTime > cutoff.low) & (d.inaccurate.removed$LogReactionTime < cutoff.high))

hist(df.outliers.removed$LogReactionTime, col="lightblue", xlab="LogReactionTime (ms)",
        main="Histogram with Normal Curve")


```


```{r}
ggplot(df.outliers.removed, aes(x=LogReactionTime, fill=Task)) +
  # facet_wrap(~BlockOrder) +
  geom_density(alpha = .4)

ggplot(df.outliers.removed, aes(x=ReactionTime, fill=Task)) +
  # facet_wrap(~BlockOrder) +
  geom_density(alpha = .4)


```






# convert everything to factors
```{r, include=FALSE, warning=FALSE, echo=FALSE}

convert_except <- function(df, exclude_cols) {
  df[] <- lapply(names(df), function(col_name) {
    if (!(col_name %in% exclude_cols)) {
      return(as.factor(df[[col_name]]))  # Convert to factor if not in excluded columns
    } else {
      return(df[[col_name]])  # Leave the excluded columns unchanged
    }
  })
  return(df)
}
# Specify columns to exclude from conversion
exclude_columns <- c('ReactionTime', 'LogReactionTime')

# Convert all columns to factors except for 'a' and 'd'
df_factors <- convert_except(df.outliers.removed, exclude_columns)

# Check the structure of the modified data frame
str(df_factors)

```


```{r, include=FALSE, warning=FALSE, echo=FALSE}
contrasts(df_factors$ConcValCombo)
contrasts(df_factors$Task)

center = df_factors %>%
  mutate(cTask = as.numeric(Task)-mean(as.numeric(Task)),
         cAccuracy = as.numeric(Accuracy)-mean(as.numeric(Accuracy)),
         cBlockOrder = as.numeric(BlockOrder)-mean(as.numeric(BlockOrder))
         )
  
  # droplevels()
```

# Is there a difference between Semantic and Valence Tasks?
Yes

```{r}

m = lmer(LogReactionTime ~ cTask + (1+cTask|ID.true) + (1+cTask|Word), data=center)
summary(m)
```

# Is there an Interaction between Task and WordType (ConcValFinal)?
No.
```{r}

m = lmer(LogReactionTime ~ cTask*ConcValCombo + (1+ConcValCombo+cTask|ID.true) + (1+cTask|Word), data=center)
# saveRDS(m, "../models/model-Task-ConcValFinal_outlier_excl_ReactionTime_corrected.rds")

# m <- readRDS("../models/model-Task-ConcValFinal_outlier_excl_ReactionTime_corrected.rds")
summary(m)
```

# Is there an Interaction between Task and WordList?
No.
```{r}

m = lmer(LogReactionTime ~ cTask*WhoseList + (1+cTask|ID.true) + (1+cTask|Word), data=center)

summary(m)
```

# Does Accuracy predict reaction time? 

In other words, is reaction time affected by certainty about the categorization?
- No.
```{r}

m = lmer(LogReactionTime ~ cAccuracyCorrected + (1|ID.true) + (1|Word), data=center)

summary(m)

```


# Main Effect of Block Order 

## On ReactionTime
- No.
```{r}
m = lmer(LogReactionTime ~ cBlockOrder + (1|ID.true) + (1+cBlockOrder|Word), data=center)

summary(m)
```



# effect of ConcValFinal on ReactionTime?
nope.
```{r}

m = lmer(LogReactionTime ~ ConcValFinal + (1+ConcValFinal|ID.true) + (1|Word), data=center)

summary(m)

```



# In the Concreteness task, is there a difference between concreteness and abstractness on ReactionTime?
- Nope
```{r}
str(df_factors)
sem <- df_factors %>% 
  filter(Task == "Concrete") %>% 
  mutate(
         Semantic = ifelse(grepl("concrete", ConcValFinal), "concrete", 
                    ifelse(grepl("abstract", ConcValFinal), "abstract", NA)),
         Valence =  ifelse(grepl("positive", ConcValFinal), "positive", 
                    ifelse(grepl("negative", ConcValFinal), "negative", NA)),
        cConcValFinal = as.numeric(ConcValFinal) - mean(as.numeric(ConcValFinal)),
        cSemantic = as.numeric(factor(Semantic)) - mean(as.numeric(factor(Semantic)))
  )

m = lmer(LogReactionTime ~ cConcValFinal + (1+cConcValFinal|ID.true) + (1+cConcValFinal|Word), data=sem)
summary(m)

```


```{r}
m = lmer(LogReactionTime ~ cSemantic + (1+cSemantic|ID.true) + (1|Word), data=sem)
summary(m)

```


# In the Valence task , is there a difference between positive and negative on ReactionTime?
- Nope.
```{r}
val <- df_factors %>% 
  filter(Task == "Valence") %>% 
  mutate(
         Semantic = ifelse(grepl("concrete", ConcValFinal), "concrete", 
                    ifelse(grepl("abstract", ConcValFinal), "abstract", NA)),
         Valence = ifelse(grepl("positive", ConcValFinal), "positive", 
                    ifelse(grepl("negative", ConcValFinal), "negative", NA)),
         cConcValFinal = as.numeric(ConcValFinal) - mean(as.numeric(ConcValFinal)),
         cValence = as.numeric(factor(Valence)) - mean(as.numeric(factor(Valence)))
         )

m = lmer(LogReactionTime ~ cConcValFinal + (1+cConcValFinal|ID.true) + (1+cConcValFinal|Word), data=val)
summary(m)

```

```{r}
m = lmer(LogReactionTime ~ cValence + (1+cValence|ID.true) + (1|Word), data=val)
summary(m)

```



