---
title: "Graphs for AccuracyCorrected"
author: "morgan moyer"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
library(stringr)
library(textstem)
library(tidyverse)
theme_set(theme_bw())
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73")
this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../../../helpers.R")

d <- read.csv("../data/corrected.csv")

names(d)

length(unique(d$Word))

```


```{r}
table(d$Task,d$Label)

print(unique(d$Word))
```



# Graph AccuracyCorrected by Word

Values for valence/concreteness were gathered/normed first from Warriner et al and 
Brysbaert et al. From those studies, we can establish what an Accurate response is.

A response is accurate (coded as 1) if the participant response was consistent with the norming study; innacurate (or 0) otherwise.

## Overall AccuracyCorrected

```{r}
agr <- d %>% 
  group_by(Task) %>% 
  reframe(MeanAccuracyCorrected = mean(AccuracyCorrected), 
          CILow = ci.low(AccuracyCorrected), 
          CIHigh = ci.high(AccuracyCorrected)) %>%
  mutate(YMin = MeanAccuracyCorrected - CILow, 
         YMax = MeanAccuracyCorrected + CIHigh)
# View(agr)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanAccuracyCorrected)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))

  # theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  # guides(fill = "none")

```

## Mean AccuracyCorrected by Word / Task
Looking at only the first block
```{r,fig.width=10, fig.height=10}
agr <- d %>%
  group_by(Task,Word,BlockOrder) %>% 
  filter((Task == "Valence") & (BlockOrder == "VC") | 
           (Task == "Concrete") & (BlockOrder == "CV")) %>% 
  mutate(MeanAccuracyCorrected = mean(AccuracyCorrected), 
          CILow = ci.low(AccuracyCorrected), 
          CIHigh = ci.high(AccuracyCorrected)) %>%
  mutate(YMin = MeanAccuracyCorrected - CILow, 
         YMax = MeanAccuracyCorrected + CIHigh)

  
agrr <- agr %>% 
  group_by(Word,Task) %>% 
  select(Word,Task,MeanAccuracyCorrected) %>% 
  unique()

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanAccuracyCorrected,fill=BlockOrder)) +
  geom_bar(position=dodge,stat="identity") +
  facet_wrap(~Word,ncol=10) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))
  # theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  # guides(fill = "none")

# View(d[(d$ID.true == c("56cc78e3ccc0e20006b82a7d")) & (d$Word == c("envy")),])
```

```{r}
m <- lmer(MeanAccuracyCorrected ~ BlockOrder + (1|Word), data =agr)
summary(m)
```


# PropPositive and PropConcrete

```{r}
val <- d %>% 
  filter(Task == "Valence") %>% 
  # filter(Word %in% conc$Word) %>% 
  group_by(Word,ConcValFinal) %>%
  mutate(Response.n = as.numeric(factor(Response, levels = c("negative", "positive"))) - 1) %>%  # Convert to numeric and subtract 1
  summarize(PropPositive = mean(Response.n))
  # filter(PropPositive > .1 | PropPositive < .9)

dodge = position_dodge(.9)
ggplot(data=val, aes(x=reorder(Word,PropPositive),y=PropPositive,fill=ConcValFinal)) +
  geom_bar(position=dodge,stat="identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")
```


```{r}
conc <- d %>% 
  filter(Task == "Concrete") %>% 
  # filter(Word %in% conc$Word) %>% 
  group_by(Word,ConcValFinal) %>%
  mutate(Response.n = as.numeric(factor(Response, levels = c("abstract", "concrete"))) - 1) %>%  # Convert to numeric and subtract 1
  summarize(PropConcrete = mean(Response.n))
  # filter(PropPositive > .1 | PropPositive < .9)

dodge = position_dodge(.9)
ggplot(data=conc, aes(x=reorder(Word,PropConcrete),y=PropConcrete,fill=ConcValFinal)) +
  geom_bar(position=dodge,stat="identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")
```

```{r}

```


## AccuracyCorrected by Participant

```{r,fig.width=10, fig.height=5}
agr <- d %>%
  # filter(PennElementType == "Selector") %>% 
  select(ID.true,Task,AccuracyCorrected) %>% 
  group_by(ID.true,Task) %>% 
  mutate(MeanAccuracyCorrected = mean(AccuracyCorrected), 
          CILow = ci.low(AccuracyCorrected), 
          CIHigh = ci.high(AccuracyCorrected)) %>%
  mutate(YMin = MeanAccuracyCorrected - CILow, 
         YMax = MeanAccuracyCorrected + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=reorder(ID.true,MeanAccuracyCorrected),y=MeanAccuracyCorrected,fill=Task)) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")

```


# Mean AccuracyCorrected by ConcValFinal

```{r}
agr <- d %>%
  group_by(Task,ConcValFinal) %>% 
  summarize(MeanAccuracyCorrected = mean(AccuracyCorrected), CILow = ci.low(AccuracyCorrected), CIHigh = ci.high(AccuracyCorrected)) %>%
  mutate(YMin = MeanAccuracyCorrected - CILow, YMax = MeanAccuracyCorrected + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanAccuracyCorrected,fill=ConcValFinal)) +
  geom_bar(position=dodge,stat="identity") +
  # facet_wrap(~Task) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))
  # theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")
```






