---
title: "Pilot 3: Reaction Time Graphs"
author: "morgan moyer"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
library(stringr)
library(textstem)
library(tidyverse)
theme_set(theme_bw())
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73")
this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../../../helpers.R")

d <- read.csv("../data/corrected.csv")
```

# Looking at overall Log ReactionTime for the data

Before removing outliers

## Summary Stats
```{r}

ggplot(d, aes(ReactionTime, fill=Task)) +
  geom_density(alpha = .5)

summary(d$ReactionTime)
```

Long tail justifies outlier removal?
```{r}
ggplot(d, aes(LogReactionTime, fill=Task)) +
  geom_density(alpha = .5)

summary(d$LogReactionTime)
```

# Remove inaccurate trials

```{r}

d.acc <- d %>% 
  filter(AccuracyCorrected == 1)

```



# LogReactionTime by Task

```{r}

agr = d.acc %>%
    group_by(Task,Word) %>%
    summarize(MeanLogReactionTime = mean(LogReactionTime), 
              CILow = ci.low(LogReactionTime), 
              CIHigh = ci.high(LogReactionTime)) %>%
    mutate(YMin = MeanLogReactionTime - CILow, 
           YMax = MeanLogReactionTime + CIHigh)

ggplot(agr, aes(x=MeanLogReactionTime, fill=Task)) +
  geom_density(alpha = .4)

ggplot(agr, aes(x=Task, y=MeanLogReactionTime,fill=Task)) + 
    geom_violin(trim=FALSE,alpha=.4) +
    geom_jitter(shape=16, position=position_jitter(0.2)) +
    # geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  # theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  guides(fill = "none")

```

# ReactionTime by Task
```{r}

agr = d.acc %>%
    group_by(Task,Word) %>%
    summarize(MeanReactionTime = mean(ReactionTime), 
              CILow = ci.low(ReactionTime), 
              CIHigh = ci.high(ReactionTime)) %>%
    mutate(YMin = MeanReactionTime - CILow, 
           YMax = MeanReactionTime + CIHigh)

ggplot(agr, aes(x=MeanReactionTime, fill=Task)) +
  geom_density(alpha = .4)

ggplot(agr, aes(x=Task, y=MeanReactionTime,fill=Task)) + 
    geom_violin(trim=FALSE,alpha=.4) +
    geom_jitter(shape=16, position=position_jitter(0.2)) +
    # geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  # theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  guides(fill = "none")

```

# LogReactionTime by BlockOrder and Task
```{r}

agr = d.acc %>%
    group_by(BlockOrder,Task,Word) %>%
    summarize(MeanLogReactionTime = mean(LogReactionTime), 
              CILow = ci.low(LogReactionTime), 
              CIHigh = ci.high(LogReactionTime)) %>%
    mutate(YMin = MeanLogReactionTime - CILow, 
           YMax = MeanLogReactionTime + CIHigh)

ggplot(agr, aes(x=MeanLogReactionTime, fill=Task)) +
  geom_density(alpha = .4)

ggplot(agr, aes(x=MeanLogReactionTime, fill=Task)) +
  facet_wrap(~BlockOrder) +
  geom_density(alpha = .4)

ggplot(agr, aes(x=Task, y=MeanLogReactionTime,fill=BlockOrder)) + 
    geom_violin(trim=FALSE,alpha=.4) +
    geom_jitter(shape=16, position=position_jitter(0.2))

```

# ReactionTime by BlockOrder and Task
```{r}

agr = d.acc %>%
    group_by(BlockOrder,Task,Word) %>%
    summarize(MeanReactionTime = mean(ReactionTime), 
              CILow = ci.low(ReactionTime), 
              CIHigh = ci.high(ReactionTime)) %>%
    mutate(YMin = MeanReactionTime - CILow, 
           YMax = MeanReactionTime + CIHigh)

ggplot(agr, aes(x=MeanReactionTime, fill=Task)) +
  geom_density(alpha = .4)

ggplot(agr, aes(x=MeanReactionTime, fill=Task)) +
  facet_wrap(~BlockOrder) +
  geom_density(alpha = .4)

ggplot(agr, aes(x=Task, y=MeanReactionTime,fill=BlockOrder)) + 
    geom_violin(trim=FALSE,alpha=.4) +
    geom_jitter(shape=16, position=position_jitter(0.2))

```


# By Item

```{r,fig.width=10, fig.height=15}
agr = d.acc %>%
    group_by(Task,Word) %>%
    summarize(MeanReactionTime = mean(ReactionTime), CILow = ci.low(ReactionTime), CIHigh = ci.high(ReactionTime)) %>%
    mutate(YMin = MeanReactionTime - CILow, YMax = MeanReactionTime + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanReactionTime,fill=Task)) +
  geom_bar(position=dodge,stat="identity") +
  facet_wrap(~Word) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))
  # theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")
```


## By ConcValFinal category and Task

### Mean Raw ReactionTime and Effects of Word Valence/Concreteness

```{r}

agr = d.acc %>%
    group_by(Task,ConcValFinal) %>%
    reframe(MeanReactionTime = mean(ReactionTime), CILow = ci.low(ReactionTime), CIHigh = ci.high(ReactionTime)) %>%
    mutate(YMin = MeanReactionTime - CILow, YMax = MeanReactionTime + CIHigh)


dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanReactionTime,fill=ConcValFinal)) +
  geom_bar(position=dodge,stat="identity") +
  # facet_wrap(~Task) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))
  # theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")


```

### Mean Raw ReactionTime and Effects of Word Valence/Concreteness

```{r}

agr = d.acc %>%
    group_by(BlockOrder,Task,ConcValFinal) %>%
    reframe(MeanReactionTime = mean(ReactionTime), CILow = ci.low(ReactionTime), CIHigh = ci.high(ReactionTime)) %>%
    mutate(YMin = MeanReactionTime - CILow, YMax = MeanReactionTime + CIHigh)


dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanReactionTime,fill=BlockOrder)) +
  geom_bar(position=dodge,stat="identity") +
  facet_wrap(~ConcValFinal) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))
  # theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")


```
