---
title: "Looking at all data p1-p5"
author: "morgan moyer"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
library(stringr)
library(textstem)
library(tidyverse)
library(kableExtra)
theme_set(theme_bw())
library(ggrepel)
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00")
this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../../../helpers.R")

p <- read.csv("../data/p1-p4.csv")
p$Accuracy <- NULL
colnames(p)[colnames(p) == "AccuracyBest"] <- "Accuracy"

ls <- read.csv("../data/p3_list_subs.csv")
# Replace ConcValCombo in d for matching Words in corrected_words

# Ensure the key column 'ID.true' exists in both dataframes
if ("ID.true" %in% names(p) && "ID.true" %in% names(ls)) {
  # Replace `WhoseList` in df where Version == "Pilot3"
  p$WhoseList[p$Version == "Pilot3"] <- ls$WhoseList[
    match(p$ID.true[p$Version == "Pilot3"], ls$ID.true)
  ]
} else {
  stop("ID.true column not found in one of the dataframes.")
}

table(p$WhoseList)

p5 <- read.csv("../data/processed.csv")
p5["Version"] <- "Pilot5"
p5["WhoseList"] <- "Combined3"

d <- bind_rows(p,p5)

unique(d$Version)
word_features <- unique(d[,c("Word","ConcValCombo")])
nrow(word_features)

table(d$WhoseList)
```


```{r}

ggplot(d, aes(x=LogReactionTime)) +
  geom_histogram(binwidth = .1,fill = "lightblue", color = "black") +
  facet_wrap(~Task)

ggplot(d, aes(x=LogReactionTime, fill=Task)) +
  geom_density(alpha = .4)

```


```{r}
agr <- d %>% 
  group_by(Task) %>% 
  reframe(MeanAccuracy = mean(Accuracy), 
          CILow = ci.low(Accuracy), 
          CIHigh = ci.high(Accuracy)) %>%
  mutate(YMin = MeanAccuracy - CILow, 
         YMax = MeanAccuracy + CIHigh)
# View(agr)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanAccuracy, fill = Task)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))

  # theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  # guides(fill = "none")

```



# Looking at Responses Generally


## Proportion Concrete
```{r}
agr <- d %>% 
  filter(Task == "Concrete") %>% 
  mutate(Response.n = as.numeric(factor(Response, levels = c("abstract", "concrete"))) - 1) %>% 
  group_by(WhoseList,ConcValCombo) %>%
  summarize(PropConcrete = mean(Response.n),
          CILow = ci.low(Response.n), 
          CIHigh = ci.high(Response.n)) %>%
  mutate(YMin = PropConcrete - CILow, 
          YMax = PropConcrete + CIHigh)


dodge = position_dodge(.9)
ggplot(data=agr, aes(x=ConcValCombo,y=PropConcrete,fill=WhoseList)) +
  geom_bar(position=dodge,stat="identity") +
  # facet_wrap(~Version) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

```{r}
agr <- d %>% 
  filter(Task == "Concrete") %>% 
  mutate(Response.n = as.numeric(factor(Response, levels = c("abstract", "concrete"))) - 1) %>% 
  group_by(Word,ConcValCombo) %>%
  summarize(PropConcrete = mean(Response.n),
            MeanReactionTime = mean(ReactionTime))


ggplot(agr, aes(x = MeanReactionTime, y = PropConcrete)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  geom_text(aes(label = Word, color = ConcValCombo), vjust = -0.5, hjust = 1.5)
  # geom_text_repel(aes(label = Word, color = ConcValCombo), 
                  vjust = -0.5, hjust = 1.5) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)

```


```{r}
agr <- d %>% 
  filter(Task == "Valence") %>% 
  mutate(Response.n = as.numeric(factor(Response, levels = c("negative", "positive"))) - 1) %>% 
  group_by(Word,ConcValCombo) %>%
  summarize(PropPositive = mean(Response.n),
            MeanReactionTime = mean(ReactionTime))


ggplot(agr, aes(x = MeanReactionTime, y = PropPositive)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  geom_text(aes(label = Word, color = ConcValCombo), vjust = -0.5, hjust = 1.5)
  # geom_text_repel(aes(label = Word, color = ConcValCombo), 
                  vjust = -0.5, hjust = 1.5) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)

```

```{r}
agr <- d %>% 
  # filter(Task == "Concrete") %>% 
  # mutate(Response.n = as.numeric(factor(Response, levels = c("abstract", "concrete"))) - 1) %>% 
  group_by(Word,Task) %>%
  summarize(MeanAccuracy = mean(Accuracy),
            MeanReactionTime = mean(ReactionTime))


ggplot(agr, aes(x = MeanReactionTime, y = MeanAccuracy)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  geom_text(aes(label = Word, color = Task), vjust = -0.5, hjust = 1.5) +
  guides(legend = "none")
  #   theme(
  #   legend.position = "top",    # Move legend to the top
  #   legend.title = element_text(size = 10),  # Adjust legend title size
  #   legend.text = element_text(size = 9)     # Adjust legend text size
  # )
  

  # geom_text_repel(aes(label = Word, color = ConcValCombo), 
                  # vjust = -0.5, hjust = 1.5) +
  # scale_fill_manual(values=cbPalette) +
  # scale_color_manual(values=cbPalette)

ggsave("../graphs/exp3_accXrt.pdf",width = 5, height = 3)

```



# Reaction Time analyses


# First Remove participants who aren't super , aggregating over Task

```{r}
length(unique(d$ID.true))
inacc.parts <- d %>% 
  group_by(ID.true) %>% 
  summarise(MeanAccuracy = mean(Accuracy)) %>% 
  filter(MeanAccuracy < .75)

# How many participants have Accuracy < .75?
length(unique(inacc.parts$ID.true))

d.inaccurate.removed <- d %>% 
  anti_join(inacc.parts, by = "ID.true")

# Sanity check
length(unique(d.inaccurate.removed$ID.true))

```

# remove all inaccurate trials
```{r}
orig <- nrow(d.inaccurate.removed)
d.inaccurate.removed <- d.inaccurate.removed %>% 
  filter(Accuracy == 1)
nrow(d.inaccurate.removed)/orig*100

```



```{r}
# Remove subjects with ReactionTime higher than 3x IQR
summary(d.inaccurate.removed$LogReactionTime)
  #  Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  # 6.924   7.328   7.436   7.479   7.579  10.008 
range(d.inaccurate.removed$LogReactionTime)

hist(d.inaccurate.removed$LogReactionTime, breaks=100, col="lightblue", xlab="LogReactionTime (ms)",
        main="Histogram with Normal Curve")

quantile(d.inaccurate.removed$LogReactionTime, na.rm = TRUE)
IQR(d.inaccurate.removed$LogReactionTime, na.rm = TRUE)*3 # 0.7526289
cutoff.high <- quantile(d.inaccurate.removed$LogReactionTime, na.rm = TRUE)[4] + IQR(d.inaccurate.removed$LogReactionTime, na.rm = TRUE)*3 # 8.419261
cutoff.low <- quantile(d.inaccurate.removed$LogReactionTime, na.rm = TRUE)[2] - IQR(d.inaccurate.removed$LogReactionTime, na.rm = TRUE)*3# 6.5088838.419261


# remove subjects with ReactionTime higher than 3 x IQR
df.outliers.removed <- subset(d.inaccurate.removed, (d.inaccurate.removed$LogReactionTime > cutoff.low) & (d.inaccurate.removed$LogReactionTime < cutoff.high))

hist(df.outliers.removed$LogReactionTime, breaks=100, col="lightblue", xlab="LogReactionTime (ms)",
        main="Histogram with Normal Curve")


```


```{r}
ggplot(df.outliers.removed, aes(x=LogReactionTime, fill=Task)) +
  # facet_wrap(~BlockOrder) +
  geom_density(alpha = .4)

ggplot(df.outliers.removed, aes(x=ReactionTime, fill=Task)) +
  # facet_wrap(~BlockOrder) +
  geom_density(alpha = .4)


```



# LogReactionTime by Task

```{r}

agr <- df.outliers.removed %>%
    group_by(Task,Word) %>%
    summarize(MeanLogReactionTime = mean(LogReactionTime), 
              CILow = ci.low(LogReactionTime), 
              CIHigh = ci.high(LogReactionTime)) %>%
    mutate(YMin = MeanLogReactionTime - CILow, 
           YMax = MeanLogReactionTime + CIHigh)

ggplot(agr, aes(x=MeanLogReactionTime, fill=Task)) +
  geom_density(alpha = .4)

ggplot(agr, aes(x=Task, y=MeanLogReactionTime,fill=Task)) + 
    geom_violin(trim=FALSE,alpha=.4) +
    geom_jitter(shape=16, position=position_jitter(0.2)) +
    # geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  # theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  guides(fill = "none")

```

# ReactionTime by Task
```{r}

agr <- df.outliers.removed %>%
    group_by(Task,Word) %>%
    summarize(MeanReactionTime = mean(ReactionTime), 
              CILow = ci.low(ReactionTime), 
              CIHigh = ci.high(ReactionTime)) %>%
    mutate(YMin = MeanReactionTime - CILow, 
           YMax = MeanReactionTime + CIHigh)

ggplot(agr, aes(x=MeanReactionTime, fill=Task)) +
  geom_density(alpha = .4)

ggplot(agr, aes(x=Task, y=MeanReactionTime,fill=Task)) + 
    geom_violin(trim=FALSE,alpha=.4) +
    geom_jitter(shape=16, position=position_jitter(0.2)) +
    # geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  # theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  guides(fill = "none")

# ggsave("../graphs/total_rt_violin.pdf",width = 4, height = 3)
```


# Whose List

```{r}
agr <- df.outliers.removed %>%
    group_by(Task,WhoseList) %>%
    reframe(MeanReactionTime = mean(ReactionTime), 
            CILow = ci.low(ReactionTime), 
            CIHigh = ci.high(ReactionTime)) %>%
    mutate(YMin = MeanReactionTime - CILow, 
           YMax = MeanReactionTime + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=reorder(WhoseList,MeanReactionTime),y=MeanReactionTime,fill=Task)) +
  geom_bar(position=dodge,stat="identity") +
  # facet_wrap(~Task) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")


table(d$WhoseList,d$Version)
```



# words that occur in multiple lists

```{r}
result <- d %>%
  group_by(Word) %>%
  filter(n_distinct(WhoseList) > 2)

length(unique(result$Word))
print(unique(result$Word))

agr <- df.outliers.removed %>% 
  filter(Word %in% result$Word) %>% 
    group_by(Task,Word,WhoseList) %>%
    summarize(MeanReactionTime = mean(ReactionTime), 
            CILow = ci.low(ReactionTime), 
            CIHigh = ci.high(ReactionTime)) %>%
    mutate(YMin = MeanReactionTime - CILow, 
           YMax = MeanReactionTime + CIHigh)

nrow(agr)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanReactionTime,fill=WhoseList)) +
  geom_bar(position=dodge,stat="identity") +
  facet_wrap(~Word) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")



```


# Take a look at the words with the 
```{r}
diff <- df.outliers.removed %>% 
  filter(!Version %in% c("Pilot1","Pilot2")) %>% 
  group_by(ID.true,Word,Task) %>% 
  mutate(
    RTDifference = abs(diff(ReactionTime[Task == "Concrete" & Task == "Valence"])) # Absolute RT difference
  )
```




# Look at cases wher RT Conc <= RT Valence

```{r}
test <- df.outliers.removed %>%
  # filter(Task %in% c("Concrete", "Valence")) %>%  # Keep only relevant tasks
  group_by(Word, Task) %>%
  summarise(
    RT = mean(ReactionTime, na.rm = TRUE),  # Take the mean RT if duplicates exist
    .groups = "drop_last" # Drop grouping by Task but keep Word and ID.true
  ) %>%
  pivot_wider(names_from = Task, values_from = RT, names_prefix = "RT_") %>% # Reshape to wide format
  filter(RT_Concrete <= RT_Valence) %>%  # Apply the condition
    pivot_longer(
    cols = starts_with("RT_"), # Select the reshaped columns
    names_to = "Task",         # Restore Task column
    names_prefix = "RT_",      # Remove "RT_" prefix to match original Task names
    values_to = "ReactionTime" # Column for the RT values
  ) %>%
  ungroup()

nrow(test)/nrow(df.outliers.removed)

```

```{r}
agr <- test %>% 
    group_by(Word, Task) %>%
    summarize(MeanReactionTime = mean(ReactionTime), 
            CILow = ci.low(ReactionTime), 
            CIHigh = ci.high(ReactionTime)) %>%
    mutate(YMin = MeanReactionTime - CILow, 
           YMax = MeanReactionTime + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanReactionTime,fill=Task)) +
  geom_bar(position=dodge,stat="identity") +
  facet_wrap(~Word) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")

```

```{r}
test_avv <- d %>% 
  filter(Word %in% test$Word) %>% 
  group_by(Word, Task) %>%
    summarize(MeanAccuracy = mean(Accuracy),
            CILow = ci.low(Accuracy), 
            CIHigh = ci.high(Accuracy),
            ) %>%
    mutate(YMin = MeanAccuracy - CILow, 
           YMax = MeanAccuracy + CIHigh)

View(test_avv)

dodge = position_dodge(.9)
ggplot(data=test_avv, aes(x=Task,y=MeanAccuracy,fill=Task)) +
  geom_bar(position=dodge,stat="identity") +
  facet_wrap(~Word) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")





```


```{r}
test_avv <- d %>% 
  filter(Word %in% test$Word) %>% 
  group_by(Word, Task) %>%
    summarize(MeanAccuracy = mean(Accuracy),
              MeanReactionTime = mean(ReactionTime))


ggplot(test_avv, aes(x = MeanReactionTime, y = MeanAccuracy)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  # geom_text(aes(label = Word, color = Task), vjust = -0.5, hjust = 1.5)
  geom_text_repel(aes(label = Word, color = Task), 
                  vjust = -0.5, hjust = 1.5) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)


```



#  Analysis
convert everything to factors
```{r, include=FALSE, warning=FALSE, echo=FALSE}
# str(d)

convert_except <- function(df, exclude_cols) {
  df[] <- lapply(names(df), function(col_name) {
    if (!(col_name %in% exclude_cols)) {
      return(as.factor(df[[col_name]]))  # Convert to factor if not in excluded columns
    } else {
      return(df[[col_name]])  # Leave the excluded columns unchanged
    }
  })
  return(df)
}
# Specify columns to exclude from conversion
exclude_columns <- c('ReactionTime', 'LogReactionTime','SecondWordLogRT')

# Convert all columns to factors except for 'a' and 'd'
df_factors <- convert_except(df.outliers.removed, exclude_columns)

# Check the structure of the modified data frame
# str(df_factors)

```


```{r, include=FALSE, warning=FALSE, echo=FALSE}
# contrasts(df_factors$SwitchCombo)
contrasts(df_factors$Task)

center = df_factors %>%
  mutate(cTask = as.numeric(Task)-mean(as.numeric(Task)),
         cAccuracy = as.numeric(Accuracy)-mean(as.numeric(Accuracy)),
         cBlockOrder = as.numeric(BlockOrder)-mean(as.numeric(BlockOrder))
         )
  
  # droplevels()
```

# Is there a difference between Semantic and Valence Tasks?
Yes

```{r}

m = lmer(LogReactionTime ~ cTask + (1+cTask|ID.true) + (1+cTask|Word), data=center)
summary(m)
```



# Is there an Interaction between Task and WordType (ConcValCombo)?
Y.
```{r}

m = lmer(LogReactionTime ~ cTask*ConcValCombo + (1+ConcValCombo+cTask|ID.true) + (1+cTask|Word), data=center)
# saveRDS(m, "../models/model-Task-ConcValCombo_outlier_excl_ReactionTime_corrected.rds")

# m <- readRDS("../models/model-Task-ConcValCombo_outlier_excl_ReactionTime_corrected.rds")
summary(m)
```

# Does Accuracy predict reaction time? 

In other words, is reaction time affected by certainty about the categorization?
- No.
```{r}

m = lmer(LogReactionTime ~ cAccuracy + (1|ID.true) + (1|Word), data=center)

summary(m)

```


# Main Effect of Block Order 

## On ReactionTime
- No.
```{r}
m = lmer(LogReactionTime ~ cBlockOrder + (1|ID.true) + (1+cBlockOrder|Word), data=center)

summary(m)
```



# effect of ConcValCombo on ReactionTime?
nope.
```{r}

m = lmer(LogReactionTime ~ ConcValCombo + (1+ConcValCombo|ID.true) + (1|Word), data=center)

summary(m)

```

#

```{r}
val <- d %>% 
  filter(Task == "Valence") %>% 
  # filter(Word %in% conc$Word) %>% 
  # select(Word,ConcValCombo,Accuracy,Response) %>% 
  group_by(Word,ConcValCombo,WhoseList) %>%
  mutate(Response.n = as.numeric(factor(Response, levels = c("negative", "positive"))) - 1) %>%  # Convert to numeric and subtract 1
  summarize(PropPositive = mean(Response.n),
            MeanAccuracy = mean(Accuracy))
  # filter(PropPositive > .1 | PropPositive < .9)

m.c <- lmer(PropPositive ~ WhoseList*ConcValCombo + (1|Word), data = val)
m.s <- lmer(PropPositive ~ ConcValCombo + (1|Word), data = val)
anova(m.c,m.s, test="LRT")
summary(m.s)

```

```{r}
rt.val <- df.outliers.removed %>% 
  filter(Task == "Valence") %>% 
  mutate(WhoseList = as.factor(WhoseList),
         Word = as.factor(Word),
         ID.true = as.factor(ID.true))

m.c <- lmer(LogReactionTime ~ WhoseList + (1|ID.true) + (1|Word), data=rt.val)

m.s <- lmer(LogReactionTime ~ cTask + (1+cTask|ID.true) + (1+cTask|Word), data=center)

anova(m.c,m.s, test="LRT")
summary(m.c)
  
```



```{r}
conc <- d %>% 
  filter(Task == "Concrete") %>% 
  # filter(Word %in% conc$Word) %>% 
  # select(Word,ConcValCombo,Accuracy,Response) %>% 
  group_by(Word,ConcValCombo,WhoseList) %>%
  mutate(Response.n = as.numeric(factor(Response, levels = c("abstract", "concrete"))) - 1) %>%  # Convert to numeric and subtract 1
  summarize(PropConcrete = mean(Response.n),
            MeanAccuracy = mean(Accuracy))
  # filter(PropPositive > .1 | PropPositive < .9)

m <- lm(PropConcrete ~ ConcValCombo, data = conc)
summary(m)


m.c <- lmer(PropConcrete ~ WhoseList*ConcValCombo + (1|Word), data = conc)
m.s <- lmer(PropConcrete ~ ConcValCombo + (1|Word), data = conc)
anova(m.c,m.s)
```


# In the Concreteness task, is there a difference between concreteness and abstractness on ReactionTime?
- Nope
```{r}
str(df_factors)
sem <- df_factors %>% 
  filter(Task == "Concrete") %>% 
  mutate(
         Semantic = ifelse(grepl("concrete", ConcValCombo), "concrete", 
                    ifelse(grepl("abstract", ConcValCombo), "abstract", NA)),
         Valence =  ifelse(grepl("positive", ConcValCombo), "positive", 
                    ifelse(grepl("negative", ConcValCombo), "negative", NA)),
        cConcValCombo = as.numeric(ConcValCombo) - mean(as.numeric(ConcValCombo)),
        cSemantic = as.numeric(factor(Semantic)) - mean(as.numeric(factor(Semantic)))
  )

m = lmer(LogReactionTime ~ cConcValCombo + (1+cConcValCombo|ID.true) + (1+cConcValCombo|Word), data=sem)
summary(m)

```


```{r}
m = lmer(LogReactionTime ~ cSemantic + (1+cSemantic|ID.true) + (1|Word), data=sem)
summary(m)

```


# In the Valence task , is there a difference between positive and negative on ReactionTime?
- Nope.
```{r}
val <- df_factors %>% 
  filter(Task == "Valence") %>% 
  mutate(
         Semantic = ifelse(grepl("concrete", ConcValCombo), "concrete", 
                    ifelse(grepl("abstract", ConcValCombo), "abstract", NA)),
         Valence = ifelse(grepl("positive", ConcValCombo), "positive", 
                    ifelse(grepl("negative", ConcValCombo), "negative", NA)),
         cConcValCombo = as.numeric(ConcValCombo) - mean(as.numeric(ConcValCombo)),
         cValence = as.numeric(factor(Valence)) - mean(as.numeric(factor(Valence)))
         )

m = lmer(LogReactionTime ~ cConcValCombo + (1+cConcValCombo|ID.true) + (1+cConcValCombo|Word), data=val)
summary(m)

```

```{r}
m = lmer(LogReactionTime ~ cValence + (1+cValence|ID.true) + (1|Word), data=val)
summary(m)

```



