---
title: "Analysis"
author: "morgan moyer"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
library(stringr)
library(textstem)
library(tidyverse)
theme_set(theme_bw())
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73")
this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../../../helpers.R")

d <- read.csv("../data/processed.csv")
d$LogRT <- log(d$RT)
d$LogReactionTime <- log(d$ReactionTime)
names(d)
```

# convert everything to factors
```{r, include=FALSE, warning=FALSE, echo=FALSE}
str(d)

convert_except <- function(df, exclude_cols) {
  df[] <- lapply(names(df), function(col_name) {
    if (!(col_name %in% exclude_cols)) {
      return(as.factor(df[[col_name]]))  # Convert to factor if not in excluded columns
    } else {
      return(df[[col_name]])  # Leave the excluded columns unchanged
    }
  })
  return(df)
}
# Specify columns to exclude from conversion
exclude_columns <- c('RT', 'LogRT','LogReactionTime','ReactionTime')

# Convert all columns to factors except for 'a' and 'd'
df_factors <- convert_except(d, exclude_columns)

# Check the structure of the modified data frame
str(df_factors)

```

```{r}
ggplot(df.outliers.removed, aes(x=LogReactionTime, fill=Task)) +
  geom_density(alpha = .4)
```


```{r, include=FALSE, warning=FALSE, echo=FALSE}
contrasts(df_factors$ConcValCombo)
contrasts(df_factors$Task)

center = df_factors %>%
  mutate(cTask = as.numeric(Task)-mean(as.numeric(Task)),
         cAccuracy = as.numeric(Accuracy)-mean(as.numeric(Accuracy)))
  
  # droplevels()
```

# Is there a difference between Semantic and Valence Tasks?
Yes.

```{r}

m = lmer(LogRT ~ cTask + (1|ID.true) + (1+cTask|Word), data=center)
# saveRDS(m.ms.ma.full, "../models/model-task-para.rds")

# m <- readRDS("../models/m.rds")
summary(m)
```

```{r}
center$LogReactionTime = as.numeric(center$LogReactionTime)

m = lmer(LogReactionTime ~ cTask + (1|ID.true) + (1+cTask|Word), data=center)
# saveRDS(m.ms.ma.full, "../models/model-task-para.rds")

# m <- readRDS("../models/m.rds")
summary(m)
```

# Is there an Interaction between Task and WordType (ConcValCombo)?
No.
```{r}

m = lmer(LogRT ~ cTask*ConcValCombo + (1+ConcValCombo|ID.true) + (1+cTask+ConcValCombo|Word), data=center)
# saveRDS(m.ms.ma.full, "../models/model-task-para.rds")

# m <- readRDS("../models/m.rds")
summary(m)
```

# Does Accuracy predict reaction time? 

In other words, is reaction time affected by certainty about the categorization?
```{r}

m = lmer(LogRT ~ cAccuracy + (1|ID.true) + (1|Word), data=center)

summary(m)

```

# Interaction between Task and Accuracy on RT?
```{r}

m = lmer(LogRT ~ cAccuracy*cTask + (1|ID.true) + (1+cTask|Word), data=center)

summary(m)

```

# Simple effect of ConcValCombo on RT?
marginal
```{r}

m = lmer(LogRT ~ ConcValCombo + (1+ConcValCombo|ID.true) + (1|Word), data=center)

summary(m)

```

Not even an interaction
```{r}

m = lmer(LogRT ~ cTask*ConcValCombo + (1+ConcValCombo|ID.true) + (1+cTask|Word), data=center)

summary(m)

```


# In the semantic task, is there a difference between concreteness and abstractness on RT?

```{r}
sem <- df_factors %>% 
  filter(Task == "semantic") %>% 
  mutate(cConcValCombo = as.numeric(ConcValCombo) - mean(as.numeric(ConcValCombo)),
         Semantic = ifelse(grepl("concrete", ConcValCombo), "concrete", 
                    ifelse(grepl("abstract", ConcValCombo), "abstract", NA)),
         Valence =  ifelse(grepl("positive", ConcValCombo), "positive", 
                    ifelse(grepl("negative", ConcValCombo), "negative", NA)),
         cSemantic = as.numeric(Semantic) - mean(as.numeric(Semantic))
         )

m = lmer(LogRT ~ cConcValCombo + (1+cConcValCombo|ID.true) + (1+cConcValCombo|Word), data=sem)
summary(m)

```


```{r}
m = lmer(LogRT ~ Semantic + (1+Semantic|ID.true) + (1|Word), data=sem)
summary(m)

```


# In the Valence task , is there a difference between positive and negative on RT?

```{r}
val <- df_factors %>% 
  filter(Task == "valence") %>% 
  mutate(cConcValCombo = as.numeric(ConcValCombo) - mean(as.numeric(ConcValCombo)),
         Semantic = ifelse(grepl("concrete", ConcValCombo), "concrete", 
                    ifelse(grepl("abstract", ConcValCombo), "abstract", NA)),
         Valence = ifelse(grepl("positive", ConcValCombo), "positive", 
                    ifelse(grepl("negative", ConcValCombo), "negative", NA)),
         cValence = as.numeric(Valence) - mean(as.numeric(Valence))
         )

m = lmer(LogRT ~ cConcValCombo + (1+cConcValCombo|ID.true) + (1+cConcValCombo|Word), data=val)
summary(m)

```

```{r}
m = lmer(LogRT ~ Valence + (1+Valence|ID.true) + (1|Word), data=val)
summary(m)

```

