---
title: "Pilot 2: Corrected Analysis without outliers"
author: "morgan moyer"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
library(stringr)
library(textstem)
library(tidyverse)
theme_set(theme_bw())
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73")
this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../../../helpers.R")

d <- read.csv("../data/corrected.csv")
```

```{r}

ggplot(d, aes(x=LogRT)) +
  geom_histogram(binwidth = .1,fill = "lightblue", color = "black") +
  facet_wrap(~Task)

ggplot(d, aes(x=LogRT, fill=Task)) +
  # facet_wrap(~BlockOrder) +
  geom_density(alpha = .4)

```


```{r}
# Remove subjects with RT higher than 3x IQR
summary(d$LogRT)
  #  Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  # 6.924   7.328   7.436   7.479   7.579  10.008 
range(d$LogRT)

hist(d$LogRT, breaks=100, col="lightblue", xlab="LogRT (ms)",
        main="Histogram with Normal Curve")

quantile(d$LogRT)
IQR(d$LogRT)*3 # 0.7526289
cutoff.high <- quantile(d$LogRT)[4] + IQR(d$LogRT)*3 # 8.419261
cutoff.low <- quantile(d$LogRT)[2] - IQR(d$LogRT)*3# 6.5088838.419261


# remove subjects with RT higher than 3 x IQR
df.outliers.removed <- subset(d, (d$LogRT > cutoff.low) & (d$LogRT < cutoff.high))

hist(df.outliers.removed$LogRT, col="lightblue", xlab="LogRT (ms)",
        main="Histogram with Normal Curve")


```


```{r}
ggplot(df.outliers.removed, aes(x=LogRT, fill=Task)) +
  # facet_wrap(~BlockOrder) +
  geom_density(alpha = .4)

ggplot(df.outliers.removed, aes(x=LogRT, fill=Task)) +
  facet_wrap(~BlockOrder) +
  geom_density(alpha = .4)

```

```{r}
ggplot(df.outliers.removed, aes(x = Accuracy, y = LogRT, fill = Task)) +
  geom_violin(alpha = 0.7) + # Violin plot
  geom_jitter(position = position_jitter(0.2), color = "black", size = 1.5, alpha = 0.5) + # Add jittered points
  labs(title = "Reaction Time by Accuracy",
       x = "Accuracy",
       y = "Reaction Time (ms)")
  # theme_minimal() +
  # theme(legend.position = "none") # Remove legend
```

# convert everything to factors
```{r, include=FALSE, warning=FALSE, echo=FALSE}
str(d)

convert_except <- function(df, exclude_cols) {
  df[] <- lapply(names(df), function(col_name) {
    if (!(col_name %in% exclude_cols)) {
      return(as.factor(df[[col_name]]))  # Convert to factor if not in excluded columns
    } else {
      return(df[[col_name]])  # Leave the excluded columns unchanged
    }
  })
  return(df)
}
# Specify columns to exclude from conversion
exclude_columns <- c('RT', 'LogRT')

# Convert all columns to factors except for 'a' and 'd'
df_factors <- convert_except(df.outliers.removed, exclude_columns)

# Check the structure of the modified data frame
str(df_factors)

```


```{r, include=FALSE, warning=FALSE, echo=FALSE}
contrasts(df_factors$ConcValCombo)
contrasts(df_factors$Task)

center = df_factors %>%
  mutate(cTask = as.numeric(Task)-mean(as.numeric(Task)),
         cAccuracy = as.numeric(Accuracy)-mean(as.numeric(Accuracy)),
         cBlockOrder = as.numeric(BlockOrder)-mean(as.numeric(BlockOrder))
         )
  
  # droplevels()
```

# Is there a difference between Semantic and Valence Tasks?
Still No effect of task.

```{r}

m = lmer(LogRT ~ cTask + (1+cTask|ID.true) + (1+cTask|Word), data=center)
# saveRDS(m.ms.ma.full, "../models/model-task-para.rds")

# m <- readRDS("../models/m.rds")
summary(m)
```

# Is there an Interaction between Task and WordType (ConcValCombo)?
No.
```{r}

m = lmer(LogRT ~ cTask*ConcValCombo + (1+ConcValCombo+cTask|ID.true) + (1+cTask+ConcValCombo|Word), data=center)
saveRDS(m, "../models/model-Task-ConcValCombo_outlier_excl.rds")

# m <- readRDS("../models/model-Task-ConcValCombo_outlier_excl.rds")
summary(m)
```

# Does Accuracy predict reaction time? 

In other words, is reaction time affected by certainty about the categorization?
- Yes, still.
```{r}

m = lmer(LogRT ~ cAccuracy + (1|ID.true) + (1|Word), data=center)

summary(m)

```

## Is the previous effect explained by task effects?
- Seems Not.
```{r}

m = lmer(LogRT ~ cAccuracy*cTask + (1+cTask|ID.true) + (1+cTask|Word), data=center)

summary(m)

```

# Is it explained by block order?
- No, but we find a main efect of block order.

```{r}

m = lmer(LogRT ~ cAccuracy*cBlockOrder + (1|ID.true) + (1+cBlockOrder|Word), data=center)

summary(m)

```

# Main Effect of Block Order 

## On RT
- Yes
```{r}
m = lmer(LogRT ~ cBlockOrder + (1|ID.true) + (1+cBlockOrder|Word), data=center)

summary(m)
```

## On Accuracy
- marginally significant
```{r}
m = lmer(cAccuracy ~ cBlockOrder + (1|ID.true) + (1+cBlockOrder|Word), data=center)

summary(m)
```



# effect of ConcValCombo on RT?
nope
```{r}

m = lmer(LogRT ~ ConcValCombo + (1+ConcValCombo|ID.true) + (1|Word), data=center)

summary(m)

```



# In the Concreteness task, is there a difference between concreteness and abstractness on RT?
- Nope
```{r}
str(df_factors)
sem <- df_factors %>% 
  filter(Task == "Concrete") %>% 
  mutate(
         Semantic = ifelse(grepl("concrete", ConcValCombo), "concrete", 
                    ifelse(grepl("abstract", ConcValCombo), "abstract", NA)),
         Valence =  ifelse(grepl("positive", ConcValCombo), "positive", 
                    ifelse(grepl("negative", ConcValCombo), "negative", NA)),
        cConcValCombo = as.numeric(ConcValCombo) - mean(as.numeric(ConcValCombo)),
        cSemantic = as.numeric(factor(Semantic)) - mean(as.numeric(factor(Semantic)))
  )

m = lmer(LogRT ~ cConcValCombo + (1+cConcValCombo|ID.true) + (1+cConcValCombo|Word), data=sem)
summary(m)

```


```{r}
m = lmer(LogRT ~ cSemantic + (1+cSemantic|ID.true) + (1|Word), data=sem)
summary(m)

```


# In the Valence task , is there a difference between positive and negative on RT?
- Nope.
```{r}
val <- df_factors %>% 
  filter(Task == "Valence") %>% 
  mutate(
         Semantic = ifelse(grepl("concrete", ConcValCombo), "concrete", 
                    ifelse(grepl("abstract", ConcValCombo), "abstract", NA)),
         Valence = ifelse(grepl("positive", ConcValCombo), "positive", 
                    ifelse(grepl("negative", ConcValCombo), "negative", NA)),
         cConcValCombo = as.numeric(ConcValCombo) - mean(as.numeric(ConcValCombo)),
         cValence = as.numeric(factor(Valence)) - mean(as.numeric(factor(Valence)))
         )

m = lmer(LogRT ~ cConcValCombo + (1+cConcValCombo|ID.true) + (1+cConcValCombo|Word), data=val)
summary(m)

```

```{r}
m = lmer(LogRT ~ cValence + (1+cValence|ID.true) + (1|Word), data=val)
summary(m)

```



