---
title: "Exploring individual differences"
author: "morgan moyer"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
library(stringr)
library(textstem)
library(tidyverse)
library(gridExtra)
theme_set(theme_bw())
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73")
this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../../../helpers.R")
```

```{r}
d <- read.csv("../data/processed.csv")
d$LogRT <- log(d$RT)
names(d)
```

# Goals

The goals of this analysis is to determine to what extent the differences we find hold within the sample of participants. 

The piloting results tell us that there are indeed task differences for RT.

To that end we can ask:

1. What percentage of the participants show this effect?

2. What percentage of items showed this effect?

```{r}
ggplot(d, aes(x=LogRT, fill=Task)) + 
  geom_density(alpha=.4) 

agr <- d %>% 
  group_by(Task) %>%
  summarize(mean = mean(RT))

View(agr)
```

# ConcValCombo

# ConcValCombo x Task x LogRT
```{r}
ggplot(d, aes(x=LogRT, fill=Task)) + 
  geom_density(alpha=.4) +
  facet_wrap(~ConcValCombo)
```



```{r}
agr = d %>%
    group_by(Task,ConcValCombo) %>%
    summarize(MeanRT = mean(RT), 
              CILow = ci.low(RT), 
              CIHigh = ci.high(RT)) %>%
    mutate(YMin = MeanRT - CILow, 
           YMax = MeanRT + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanRT,fill=Task)) +
  geom_bar(position=dodge,stat="identity") +
  facet_wrap(~ConcValCombo) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))
  # theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Task x ConcValCombo x Mean Accuracy
```{r}
agr = d %>%
    group_by(Task,ConcValCombo) %>%
    summarize(MeanAccuracy = mean(Accuracy), 
              CILow = ci.low(Accuracy), 
              CIHigh = ci.high(Accuracy)) %>%
    mutate(YMin = MeanAccuracy - CILow, 
           YMax = MeanAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanAccuracy,fill=Task)) +
  geom_bar(position=dodge,stat="identity") +
  facet_wrap(~ConcValCombo) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))
  # theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

#### Acuracy by-item
```{r}
agr = d %>%
    group_by(Task,ConcValCombo,Word) %>%
    summarize(MeanAccuracy = mean(Accuracy))
            

ggplot(agr, aes(x=MeanAccuracy, fill=ConcValCombo)) + 
  geom_density(alpha=.4) +
  facet_wrap(~Task)
```

```{r}
ggplot(agr, aes(x=MeanAccuracy, fill=Task)) + 
  geom_density(alpha=.4) +
  facet_wrap(~ConcValCombo)
```


### Accuracy by-participant
```{r}
agr = d %>%
    # filter(Task == "valence") %>% 
    group_by(Task,ConcValCombo,ID.true) %>%
    summarize(MeanAccuracy = mean(Accuracy))
              
ggplot(agr, aes(x=MeanAccuracy, fill=ConcValCombo)) + 
  geom_density(alpha=.4) +
  facet_wrap(~Task)
```

```{r}
ggplot(agr, aes(x=MeanAccuracy, fill=Task)) + 
  geom_density(alpha=.4) +
  facet_wrap(~ConcValCombo)
```




# Differences by-item, aggregating over participants

- Biggest differences for: disappoint, discourage, feeling, fogive, frown, laugh, sail, sing, smack, specialize, violate, wish

- Least differences for: befall, behold, consider, crank, envy, hurl, impose, lick, meth, running, talk, 


Some "surprising" differences
- HURL: doesn't seem to have a difference
- VIOLATE: has a huge difference
--> is the difference for VIOLATE a function of exteme emotive component as compared to HURL? Like, visceral


Generalization: In no case is the peak for Semantic Task === except for FEELING === higher than the peak for valence.


```{r, fig.width=10, fig.height=15}
ggplot(d, aes(x=LogRT, fill=Task)) + 
  geom_density(alpha=.4) +
  facet_wrap(~Word,ncol=4)
```

```{r, fig.width=10, fig.height=15}
agr = d %>%
    group_by(Task,Word) %>%
    summarize(MeanRT = mean(RT), 
              CILow = ci.low(RT), 
              CIHigh = ci.high(RT)) %>%
    mutate(YMin = MeanRT - CILow, 
           YMax = MeanRT + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanRT,fill=Task)) +
  geom_bar(position=dodge,stat="identity") +
  facet_wrap(~Word,ncol=4) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))
  # theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r, eval=FALSE, echo=FALSE}

# First, create the density plot
density_plot <- ggplot(d, aes(x = LogRT, fill = Task)) + 
  geom_density(alpha = 0.4) +
  facet_wrap(~ Word, ncol = 2) +
  theme_minimal() +
  labs(title = "Density Plot of LogRT by Task")

# Now create the bar plot with error bars
agr <- d %>%
  group_by(Task, Word) %>%
  summarize(
    MeanRT = mean(RT), 
    CILow = ci.low(RT), 
    CIHigh = ci.high(RT)
  ) %>%
  mutate(YMin = MeanRT - CILow, YMax = MeanRT + CIHigh)

dodge <- position_dodge(0.9)
bar_plot <- ggplot(data = agr, aes(x = Task, y = MeanRT, fill = Task)) +
  geom_bar(position = dodge, stat = "identity") +
  facet_wrap(~ Word, ncol = 2) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax), width = 0.25, position = dodge) +
  theme_minimal() +
  labs(title = "Mean RT by Task with Error Bars")

# Combine the two plots side-by-side
grid.arrange(density_plot, bar_plot, ncol = 2)

```



```{r, eval=FALSE, echo=FALSE}
# Prepare summary data for bar plot (mean RT and CI)
agr <- d %>%
  group_by(Task, Word) %>%
  summarize(
    MeanLogRT = mean(LogRT), 
    CILow = ci.low(LogRT), 
    CIHigh = ci.high(LogRT)
  ) %>%
  mutate(YMin = MeanLogRT - CILow, YMax = MeanLogRT + CIHigh)

# Create the combined plot
ggplot() + 
  # Density plot
  geom_density(data = d, aes(x = LogRT, fill = Task)) + # , alpha = 0.4
  
  # Bar plot (Mean RT with error bars)
  geom_bar(data = agr, aes(x = Task, y = MeanLogRT, fill = Task), 
           stat = "identity", position = position_dodge(0.9), alpha = 0.7) +
  geom_errorbar(data = agr, aes(x = Task, ymin = YMin, ymax = YMax), 
                width = 0.25, position = position_dodge(0.9)) +
  
  # Facet by Word with each Word on a separate row
  facet_wrap(~ Word, ncol = 2, scales = "free_y") +
  
  # Styling
  theme_minimal() +
  labs(x = "LogRT and Task", y = "Density / Mean RT", 
       title = "Density and Mean RT Plots by Word") +
  theme(strip.text = element_text(size = 12), 
        axis.text.x = element_text(angle = 45, hjust = 1))

```




```{r, eval=FALSE, echo=FALSE}
# Load necessary packages
library(dplyr)
library(rstatix)
library(purrr)

# Define the function for non-parametric pairwise comparisons
pairwise_comparisons <- function(data) {
  
  # Perform pairwise comparisons for each unique Word
  results <- data %>%
    group_by(Word) %>%   # Group data by Word
    nest() %>%           # Nest the data for each Word
    mutate(pairwise_test = map(data, ~wilcox_test(LogRT ~ Task, data = .x, paired = TRUE) %>%
                                 adjust_pvalue(method = "bonferroni"))) %>%
    select(Word, pairwise_test) %>%
    unnest(pairwise_test)   # Unnest the results
  
  return(results)
}

# Usage Example (assuming you have a dataframe `d` with columns Word, LogRT, and Task)
results <- pairwise_comparisons(d)
ncol=4results)

```


<!-- # convert ev erything to factors -->
```{r, include=FALSE, warning=FALSE, echo=FALSE, eval=FALSE}
str(d)

convert_except <- function(df, exclude_cols) {
  df[] <- lapply(names(df), function(col_name) {
    if (!(col_name %in% exclude_cols)) {
      return(as.factor(df[[col_name]]))  # Convert to factor if not in excluded columns
    } else {
      return(df[[col_name]])  # Leave the excluded columns unchanged
    }
  })
  return(df)
}
# Specify columns to exclude from conversion
exclude_columns <- c('RT', 'LogRT')

# Convert all columns to factors except for 'a' and 'd'
df_factors <- convert_except(d, exclude_columns)

# Check the structure of the modified data frame
str(df_factors)


contrasts(df_factors$ConcValCombo)
contrasts(df_factors$Task)

center = df_factors %>%
  mutate(cTask = as.numeric(Task)-mean(as.numeric(Task)),
         cAccuracy = as.numeric(Accuracy)-mean(as.numeric(Accuracy)))
```


# Looking at specific items

First, the clear cases where we see what we expected to find, then some other interesting cases


## Clear cases

### VIOLATE


```{r}
agr = d %>%
  filter(Word == "violate") %>% 
    group_by(Task) %>%
    summarize(MeanAccuracy = mean(Accuracy),
              MeanLogRT = mean(LogRT),
              Variance = var(LogRT))
              
print(agr)

ggplot(d[d$Word=="violate",], aes(x=LogRT, fill=Task)) + 
  geom_density(alpha=.4)

```

### DISAPPOINT

```{r}
agr = d %>%
  filter(Word == "disappoint") %>% 
    group_by(Task) %>%
    summarize(MeanAccuracy = mean(Accuracy),
              MeanLogRT = mean(LogRT),
              Variance = var(LogRT))
             
print(agr)

ggplot(d[d$Word=="disappoint",], aes(x=LogRT, fill=Task)) + 
  geom_density(alpha=.4)

```

### FROWN
Should be clearly concrete, but accuracy at chance
```{r}
agr = d %>%
  filter(Word == "frown") %>% 
    group_by(Task) %>%
    summarize(MeanAccuracy = mean(Accuracy),
              MeanLogRT = mean(LogRT),
              Variance = var(LogRT))
              
print(agr)

ggplot(d[d$Word=="frown",], aes(x=LogRT, fill=Task)) + 
  geom_density(alpha=.4)
```

### LAUGH

- More accurate for semantictask, but still longer RT
- low variance

```{r}
agr = d %>%
  filter(Word == "laugh") %>% 
    group_by(Task) %>%
    summarize(MeanAccuracy = mean(Accuracy),
              MeanLogRT = mean(LogRT),
              Variance = var(LogRT))
              
print(agr)

ggplot(d[d$Word=="laugh",], aes(x=LogRT, fill=Task)) + 
  geom_density(alpha=.4)

```

## Cases where there are No RT differences between Task
### IMPOSE

```{r}
agr = d %>%
  filter(Word == "impose") %>% 
    group_by(Task) %>%
    summarize(MeanAccuracy = mean(Accuracy),
              MeanLogRT = mean(LogRT),
              Variance = var(LogRT))
              
print(agr)

ggplot(d[d$Word=="impose",], aes(x=LogRT, fill=Task)) + 
  geom_density(alpha=.4)
```

## Mabe some surprising results?

### HURL
expected to be very concrete, and very negative
- high variance
```{r}
agr = d %>%
  filter(Word == "hurl") %>% 
    group_by(Task) %>%
    summarize(MeanAccuracy = mean(Accuracy),
              MeanLogRT = mean(LogRT),
              Variance = var(LogRT))
              
print(agr)

ggplot(d[d$Word=="hurl",], aes(x=LogRT, fill=Task)) + 
  geom_density(alpha=.4)

```


### FEELING
- don't really have clear expectations
- higher variance in Semantic task versus Valence task
```{r}
agr = d %>%
  filter(Word == "feeling") %>% 
    group_by(Task) %>%
    summarize(MeanAccuracy = mean(Accuracy),
              MeanLogRT = mean(LogRT),
              Variance = var(LogRT))
              
print(agr)

ggplot(d[d$Word=="feeling",], aes(x=LogRT, fill=Task)) + 
  geom_density(alpha=.4)

```



# Differences by participant

## Semantic Task

### ConcValCombo Mean Accuracy

```{r}

agr = d %>%
    filter(Task == "semantic") %>% 
    group_by(ConcValCombo,ID.true) %>%
    summarize(MeanAccuracy = mean(Accuracy))
              
ggplot(agr, aes(x=MeanAccuracy, fill=ConcValCombo)) + 
  geom_density(alpha=.4)
```

### ConcValCombo at (Log) RT

```{r}
agr = d %>%
    filter(Task == "semantic") %>% 
    group_by(ConcValCombo,ID.true) %>%
    summarize(MeanLogRT = mean(LogRT),
              MeanRT = mean(RT))
              
ggplot(agr, aes(x=MeanLogRT, fill=ConcValCombo)) + 
  geom_density(alpha=.4)

ggplot(agr, aes(x=MeanRT, fill=ConcValCombo)) + 
  geom_density(alpha=.4)

```


### ConcValCombo x RT by-participant

Lots of differences, unlclear if anything is consistent

```{r}
agr = d %>%
  filter(Task == "semantic") %>% 
    group_by(ID.true,ConcValCombo) %>%
    summarize(MeanRT = mean(RT), 
              CILow = ci.low(RT), 
              CIHigh = ci.high(RT)) %>%
    mutate(YMin = MeanRT - CILow, 
           YMax = MeanRT + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=ID.true,y=MeanRT,fill=ID.true)) +
  geom_bar(position=dodge,stat="identity") +
  facet_wrap(~ConcValCombo) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))+
  # ylim(5,8) +
  guides(fill = "none") +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

```{r, fig.width=10, fig.height=15}
dodge = position_dodge(.9)
ggplot(data=agr, aes(x=ConcValCombo,y=MeanRT,fill=ConcValCombo)) +
  geom_bar(position=dodge,stat="identity") +
  facet_wrap(~ID.true) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))+
  # ylim(5,8) +
  guides(fill = "none") +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```



### ConcValCombo x Accuracy, by-participant

LOTS of variance

```{r}
agr = d %>%
  filter(Task == "semantic") %>% 
    group_by(ID.true,ConcValCombo) %>%
    summarize(MeanAccuracy = mean(Accuracy), 
              CILow = ci.low(Accuracy), 
              CIHigh = ci.high(Accuracy)) %>%
    mutate(YMin = MeanAccuracy - CILow, 
           YMax = MeanAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=ID.true,y=MeanAccuracy,fill=ID.true)) +
  geom_bar(position=dodge,stat="identity") +
  facet_wrap(~ConcValCombo) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))+
  # ylim(5,8) +
  guides(fill = "none") +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

```{r, fig.width=10, fig.height=15}

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=ConcValCombo,y=MeanAccuracy,fill=ConcValCombo)) +
  geom_bar(position=dodge,stat="identity") +
  facet_wrap(~ID.true) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))+
  # ylim(5,8) +
  guides(fill = "none") +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```




## by-participant, by-item
```{r, fig.width=10, fig.height=15}
agr = d %>%
  filter(Task == "semantic") %>% 
    group_by(ID.true,Word) %>%
    summarize(MeanLogRT = mean(LogRT), 
              CILow = ci.low(LogRT), 
              CIHigh = ci.high(LogRT)) %>%
    mutate(YMin = MeanLogRT - CILow, 
           YMax = MeanLogRT + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=ID.true,y=MeanLogRT,fill=ID.true)) +
  geom_bar(position=dodge,stat="identity") +
  facet_wrap(~Word,ncol=4) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))+
  # ylim(5,8) +
  guides(fill = "none") +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```


```{r, fig.width=10, fig.height=15}
agr = d %>%
  filter(Task == "semantic") %>% 
    group_by(ID.true,Word) %>%
    summarize(MeanAccuracy = mean(Accuracy), 
              CILow = ci.low(Accuracy), 
              CIHigh = ci.high(Accuracy)) %>%
    mutate(YMin = MeanAccuracy - CILow, 
           YMax = MeanAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=ID.true,y=MeanAccuracy,fill=ID.true)) +
  geom_bar(position=dodge,stat="identity") +
  facet_wrap(~Word,ncol=4) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))+
  # ylim(5,8) +
  guides(fill = "none") +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))

```


## Valence Task


### ConcValCombo x Mean Accuracy

```{r}

agr = d %>%
    filter(Task == "valence") %>% 
    group_by(ConcValCombo,ID.true) %>%
    summarize(MeanAccuracy = mean(Accuracy))
              
ggplot(agr, aes(x=MeanAccuracy, fill=ConcValCombo)) + 
  geom_density(alpha=.4)
```

### ConcValCombo x (Log) RT

```{r}
agr = d %>%
    filter(Task == "valence") %>% 
    group_by(ConcValCombo,ID.true) %>%
    summarize(MeanLogRT = mean(LogRT),
              MeanRT = mean(RT))
              
ggplot(agr, aes(x=MeanLogRT, fill=ConcValCombo)) + 
  geom_density(alpha=.4)

ggplot(agr, aes(x=MeanRT, fill=ConcValCombo)) + 
  geom_density(alpha=.4)

```

### ConcValCombo x RT by-participant

```{r}
agr = d %>%
  filter(Task == "valence") %>% 
    group_by(ID.true,ConcValCombo) %>%
    summarize(MeanRT = mean(RT), 
              CILow = ci.low(RT), 
              CIHigh = ci.high(RT)) %>%
    mutate(YMin = MeanRT - CILow, 
           YMax = MeanRT + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=ID.true,y=MeanRT,fill=ID.true)) +
  geom_bar(position=dodge,stat="identity") +
  facet_wrap(~ConcValCombo) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))+
  # ylim(5,8) +
  guides(fill = "none") +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

```{r, fig.width=10, fig.height=15}
dodge = position_dodge(.9)
ggplot(data=agr, aes(x=ConcValCombo,y=MeanRT,fill=ConcValCombo)) +
  geom_bar(position=dodge,stat="identity") +
  facet_wrap(~ID.true) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))+
  # ylim(5,8) +
  guides(fill = "none") +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```



### ConcValCombo x Accuracy, by-participant

```{r}
agr = d %>%
  filter(Task == "valence") %>% 
    group_by(ID.true,ConcValCombo) %>%
    summarize(MeanAccuracy = mean(Accuracy), 
              CILow = ci.low(Accuracy), 
              CIHigh = ci.high(Accuracy)) %>%
    mutate(YMin = MeanAccuracy - CILow, 
           YMax = MeanAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=ID.true,y=MeanAccuracy,fill=ID.true)) +
  geom_bar(position=dodge,stat="identity") +
  facet_wrap(~ConcValCombo) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))+
  # ylim(5,8) +
  guides(fill = "none") +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

```{r, fig.width=10, fig.height=15}

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=ConcValCombo,y=MeanAccuracy,fill=ConcValCombo)) +
  geom_bar(position=dodge,stat="identity") +
  facet_wrap(~ID.true) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))+
  # ylim(5,8) +
  guides(fill = "none") +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```




# By participant, by Item
```{r, fig.width=10, fig.height=15}
agr = d %>%
  filter(Task == "valence") %>% 
    group_by(ID.true,Word) %>%
    summarize(MeanRT = mean(RT), CILow = ci.low(RT), CIHigh = ci.high(RT)) %>%
    mutate(YMin = MeanRT - CILow, YMax = MeanRT + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=ID.true,y=MeanRT,fill=ID.true)) +
  geom_bar(position=dodge,stat="identity") +
  facet_wrap(~Word) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))+
  # ylim(5,8) +
  guides(fill = "none") +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

```{r, fig.width=10, fig.height=15}
agr = d %>%
  filter(Task == "valence") %>% 
    group_by(ID.true,Word) %>%
    summarize(MeanAccuracy = mean(Accuracy), 
              CILow = ci.low(Accuracy), 
              CIHigh = ci.high(Accuracy)) %>%
    mutate(YMin = MeanAccuracy - CILow, 
           YMax = MeanAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=ID.true,y=MeanAccuracy,fill=ID.true)) +
  geom_bar(position=dodge,stat="identity") +
  facet_wrap(~Word,ncol=4) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))+
  # ylim(5,8) +
  guides(fill = "none") +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))

```


# One by one Graphs 


```{r, fig.width=15}

plot_by_word <- function(data) {
  # Get the unique Words
  unique_words <- unique(data$Word)
  
  # Iterate over each Word and create a plot
  for (word in unique_words) {
    # Filter data for the current Word
    data_filtered <- data %>%
      filter(Word == word) %>%
      group_by(Task, ID.true,Word) %>%
      summarize(MeanRT = mean(RT), 
                CILow = ci.low(RT), 
                CIHigh = ci.high(RT)) %>%
      mutate(YMin = MeanRT - CILow, 
             YMax = MeanRT + CIHigh)
    
    # Generate the plot for the current Word
    p <- ggplot(data_filtered, aes(x = ID.true, y = MeanRT, alpha = Task)) +
      geom_bar(position=dodge,stat="identity") +
      geom_errorbar(aes(ymin = YMin, ymax = YMax), width = 0.25, position = position_dodge(0.9) ) +  # Error bars
      # facet_wrap(~Task) +
      labs(title = paste("Mean RT for Word:", word), 
           x = NULL,  # Remove x-axis label
           y = "RT") +  # Add y-axis label
      guides(fill = "none")
      # theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Tilt x-axis labels
    
    # Print the plot
    print(p)
  }
}

# Usage Example (assuming `d` is your dataframe)
plot_by_word(d)


```