---
title: "Graphs"
author: "morgan moyer"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
library(stringr)
library(textstem)
library(tidyverse)
theme_set(theme_bw())
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73")
this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../../../helpers.R")
```

```{r}
d <- read.csv("../data/processed.csv")
```



# Graph Accuracy by Word

Values for valence/concreteness were gathered/normed first from Warriner et al and 
Brysbaert et al. From those studies, we can establish what an Accurate response is.

A response is accurate (coded as 1) if the participant response was consistent with the norming study; innacurate (or 0) otherwise.

## Overall Accuracy
```{r}
agr <- d %>% 
  group_by(Task) %>% 
  reframe(meanAccuracy = mean(Accuracy))
View(agr)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=meanAccuracy)) +
  geom_bar(position=dodge,stat="identity")
  # theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  # guides(fill = "none")

```

## Mean Accuracy by Word
```{r}
agr <- d %>%
  # filter(PennElementType == "Selector") %>% 
  # select(ID.true,Word,Accuracy) %>% 
  group_by(Word) %>% 
  mutate(MeanAccuracy_byWord = mean(Accuracy))

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=reorder(Word,MeanAccuracy_byWord),y=MeanAccuracy_byWord,fill=Word)) +
  geom_bar(position=dodge,stat="identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  guides(fill = "none")

# View(d[(d$ID.true == c("56cc78e3ccc0e20006b82a7d")) & (d$Word == c("envy")),])
```

## Accuracy by Participant

Participants seem to be performing at chance....
```{r}
agr <- d %>%
  # filter(PennElementType == "Selector") %>% 
  select(ID.true,Word,Accuracy) %>% 
  group_by(ID.true) %>% 
  mutate(MeanAccuracy_bySubject = mean(Accuracy))

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=reorder(ID.true,MeanAccuracy_bySubject),y=MeanAccuracy_bySubject,fill=ID.true)) +
  geom_bar(position=dodge,stat="identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  guides(fill = "none")

```


## Mean Accuracy by Word and Task
```{r}
agr <- d %>%
  group_by(Task,Word) %>% 
  summarize(MeanAccuracy_byWord = mean(Accuracy), CILow = ci.low(Accuracy), CIHigh = ci.high(Accuracy)) %>%
  mutate(YMin = MeanAccuracy_byWord - CILow, YMax = MeanAccuracy_byWord + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=reorder(Word,MeanAccuracy_byWord),y=MeanAccuracy_byWord,fill=Task)) +
  geom_bar(position=dodge,stat="identity") +
  # facet_wrap(~Task) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  guides(fill = "none")

```


# Looking at overall Log RT for the data

Before removing outliers

## Summary Stats
```{r}

ggplot(d, aes(RT, fill=Task)) +
  geom_density(alpha = .5)

summary(d$RT)

# Create a column for logRT
d$LogRT <- log(d$RT)

ggplot(d, aes(LogRT, fill=Task)) +
  geom_density(alpha = .5)

summary(d$LogRT)
```

```{r}

agr = d %>%
    group_by(Task,Word) %>%
    summarize(MeanLogRT = mean(LogRT), CILow = ci.low(LogRT), CIHigh = ci.high(LogRT)) %>%
    mutate(YMin = MeanLogRT - CILow, YMax = MeanLogRT + CIHigh)

ggplot(agr, aes(x=MeanLogRT, fill=Task)) +
  geom_density(alpha = .4)

ggplot(agr, aes(x=Task, y=MeanLogRT,fill=Task)) + 
    geom_violin(trim=FALSE,alpha=.4) +
    geom_jitter(shape=16, position=position_jitter(0.2)) +
    # geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  # theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  guides(fill = "none")

```



```{r}
agr = d %>%
    group_by(Task,Word) %>%
    summarize(MeanLogRT = mean(LogRT), CILow = ci.low(LogRT), CIHigh = ci.high(LogRT)) %>%
    mutate(YMin = MeanLogRT - CILow, YMax = MeanLogRT + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Word,y=MeanLogRT,fill=Task)) +
  geom_bar(position=dodge,stat="identity") +
  # facet_wrap(~Task) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")


ggplot(agr, aes(x=Word, y=MeanLogRT,fill=Task)) + 
    geom_boxplot(alpha=.4) +
    geom_jitter(shape=16, position=position_jitter(0.2)) +
    geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # geom_boxplot()
  # guides(fill = "none", alpha = "none")
  # ylim(0,1)
```




## By ConcValCombo category and Task

### Mean LogRT and Effects of Word Valence/Concreteness
```{r}
agr = d %>%
    group_by(Task,ConcValCombo) %>%
    reframe(MeanLogRT = mean(LogRT), CILow = ci.low(LogRT), CIHigh = ci.high(LogRT)) %>%
    mutate(YMin = MeanLogRT - CILow, YMax = MeanLogRT + CIHigh)


dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanLogRT,fill=ConcValCombo)) +
  geom_bar(position=dodge,stat="identity") +
  # facet_wrap(~Task) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))
  # theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  # guides(fill = "none")

```

### Mean Raw RT and Effects of Word Valence/Concreteness

```{r}

agr = d %>%
    group_by(Task,ConcValCombo) %>%
    reframe(MeanRT = mean(RT), CILow = ci.low(RT), CIHigh = ci.high(RT)) %>%
    mutate(YMin = MeanRT - CILow, YMax = MeanRT + CIHigh)


dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanRT,fill=ConcValCombo)) +
  geom_bar(position=dodge,stat="identity") +
  # facet_wrap(~Task) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")


```
