---
title: "Analysis of Arousal"
author: "author"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
library(stringr)
library(textstem)
library(tidyverse)
library(kableExtra)
library(emmeans)
library(ggeffects)
theme_set(theme_bw())
library(ggrepel)
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00")
this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../../helpers.R")

# v1 <- read_csv("../../01_verbs/exploratory_all_data/data/processed.csv")
# v1["Category"] <- "Verbs"

v <- read_csv("../../01_concreteness/01_verbs/data/processed.csv")
v["Category"] <- "Verbs"
v["Experiment"] <- "Ex1a: Conc-Abs (Verbs)"

n <- read_csv("../../01_concreteness/02_nouns/data/processed.csv")
n["Category"] <- "Nouns"
n["Experiment"] <- "Ex1b: Conc-Abs (Nouns)"

a <- read_csv("../../01_concreteness/03_adjectives/data/processed.csv")
a["Category"] <- "Adjs"
a["Experiment"] <- "Ex1c: Conc-Abs (Adjs)"

a2 <- read_csv("../../03_phys-soc/01_experiment/data/processed.csv")
a2["Category"] <- "Adjs"
a2["Experiment"] <- "Ex2b: Phys-Soc (Adjs)"

v2 <- read_csv("../../02_phys-psych/01_experiment/data/processed.csv")
v2["Category"] <- "Verbs"
v2["Experiment"] <- "Ex2a: Phys-Psych (Verbs)"


n2 <- read_csv("../../04_animacy/01_experiment/data/processed.csv")
n2["Category"] <- "Nouns"
n2["Experiment"] <- "Ex3: Animacy (Nouns)"

s <- read_csv("../../05_syntactic/01_experiment/data/processed.csv")
s["Experiment"] <- "Ex4: Syntactic (N v. V)"

arousal <- read_csv("../data/total_words_measures.csv")

d <- bind_rows(v,n,a,a2,v2,n2,s)
nrow(d)
dt <- merge(d,arousal, by=c("Word","Experiment"))
nrow(dt)

```


```{r}

df <- anti_join(d,dt)
print(unique(df$Word))

nrow(df)
length(unique(df$Word))
# table(df$Word,df$Experiment)

length(unique(dt$Word))
# table(df$Word,df$Experiment)
```

# Nested Model Comparison

## Remove outliers

```{r}
# First remove inaccurate participants
length(unique(d$ID.true))
inacc.parts <- dt %>% 
  group_by(Experiment,ID.true,Task,Category) %>% 
  summarise(MeanAccuracy = mean(Accuracy)) %>% 
  filter(MeanAccuracy < .75)
# How many participants have Accuracy < .75?
length(unique(inacc.parts$ID.true))
# Remove them
d.inaccurate.removed <- dt %>% 
  anti_join(inacc.parts, by = "ID.true")
# Sanity check
length(unique(d.inaccurate.removed$ID.true))


# Second, remove all inaccurate trials
orig <- nrow(d.inaccurate.removed)
d.inaccurate.removed <- d.inaccurate.removed %>% 
  filter(Accuracy == 1)
nrow(d.inaccurate.removed)/orig*100


quantile(d.inaccurate.removed$LogReactionTime, na.rm = TRUE)
IQR(d.inaccurate.removed$LogReactionTime, na.rm = TRUE)*3 # 0.7526289
cutoff.high <- quantile(d.inaccurate.removed$LogReactionTime, na.rm = TRUE)[4] + IQR(d.inaccurate.removed$LogReactionTime, na.rm = TRUE)*3 # 8.419261
cutoff.low <- quantile(d.inaccurate.removed$LogReactionTime, na.rm = TRUE)[2] - IQR(d.inaccurate.removed$LogReactionTime, na.rm = TRUE)*3# 6.5088838.419261

# remove subjects with ReactionTime higher than 3 x IQR
df.outliers.removed <- subset(d.inaccurate.removed, (d.inaccurate.removed$LogReactionTime > cutoff.low) & (d.inaccurate.removed$LogReactionTime < cutoff.high))
```

# Are arousal and valence corellated?

```{r}

ggplot(df.outliers.removed, aes(x = V.Mean.Sum, y = A.Mean.Sum)) +
  geom_point(alpha = 0.4) +
  geom_smooth(method = "lm",
              formula = y ~ poly(x, 2),
              se = TRUE) +
  theme_classic(base_size = 14)
```


```{r}
cor.test(df.outliers.removed$V.Mean.Sum, df.outliers.removed$A.Mean.Sum)
```



```{r}

dcen <- df.outliers.removed %>% 
  mutate(
         Task = ifelse(Task == "Valence", "Valence", "TruthCond"),
         Task = factor(Task, levels = c("TruthCond","Valence")),
         cTask = as.numeric(Task)-mean(as.numeric(Task)),
         Word = as.factor(Word),
         ID.true = as.factor(ID.true),
         Experiment = as.factor(Experiment)
         )

```


```{r}
m_base <- lmer(
  LogReactionTime ~ Task * Experiment +
    (1 | Word) +
    (1 | ID.true),
  data = dcen
)

m_arousal <- lmer(
  LogReactionTime ~ Task * Experiment * A.Mean.Sum +
    (1 | Word) +
    (1 | ID.true),
  data = dcen
)

m_valence <- lmer(
  LogReactionTime ~ Task * Experiment * V.Mean.Sum +
    (1 | Word) + (1 | ID.true),
  data = dcen
)
```

## Does arousal improve fit over baseline?
```{r}
anova(m_base,m_arousal)
```


## Does arousal modulate Task ? (interaction?)
```{r}
summary(m_arousal)
```


## Does valence improve fit over baseline?
```{r}
anova(m_base,m_valence)
```

## Does valence modulate Task ? (interaction?)
```{r}
summary(m_valence)
```


# does arousal add anything beyone valence?

```{r}
m_both <- lmer(
  LogReactionTime ~ Task * Experiment + A.Mean.Sum + V.Mean.Sum +
    (1 | Word) + (1 | ID.true),
  data = dcen
)
```

```{r}
anova(m_valence, m_both)
```

# Does valence add anything beoyond arousal?

```{r}
anova(m_arousal, m_both)
```

# Which is a stronger predictor overall?

```{r}
anova(m_valence, m_arousal)
```


# Does arousal compete with task?
```{r}

m_full <- lmer(
  LogReactionTime ~ Task * Experiment + A.Mean.Sum * Task +
    (1 | Word) + (1 | ID.true),
  data = dcen
)
```

```{r}
anova(m_base, m_full)
```


# Directionality?

```{r}
emmeans(m_arousal, ~ A.Mean.Sum | Task)
plot(ggpredict(m_arousal, terms = c("A.Mean.Sum", "Task")))
```

```{r}
emmeans(m_valence, ~ V.Mean.Sum | Task)
plot(ggpredict(m_valence, terms = c("V.Mean.Sum", "Task")))
```

```{r}
emtrends(m_arousal, ~ Task, var = "A.Mean.Sum")
emtrends(m_valence, ~ Task, var = "V.Mean.Sum")
```

```{r}
emmip(m_arousal, Task ~ A.Mean.Sum, cov.reduce = range)
emmip(m_valence, Task ~ V.Mean.Sum, cov.reduce = range)
```

### are they formally different?
```{r}
pairs(emtrends(m_arousal, ~ Task, var = "A.Mean.Sum"))
```


## Is it driven by Experiment?


```{r}
emtrends(m_arousal, ~ Task | Experiment, var = "A.Mean.Sum")
```


```{r}
# Compare TruthCond vs Valence slopes, separately for each Experiment
pairs(emtrends(m_arousal, ~ Task | Experiment, var = "A.Mean.Sum"), by = "Experiment")
```


```{r}
# Test if the Task contrast differs across Experiments
emt <- emtrends(m_arousal, ~ Task * Experiment, var = "A.Mean.Sum")
contrast(emt, interaction = "pairwise", by = NULL)
```


```{r}
emmip(m_arousal, Experiment * Task ~ A.Mean.Sum, cov.reduce = range)
```

```{r}
emmip(m_arousal, Experiment ~ A.Mean.Sum | Task, cov.reduce = range)
```

```{r}
emmip(m_arousal, Task ~ A.Mean.Sum | Experiment, cov.reduce = range)
```

