---
title: "Everything: Order Effects"
author: "author"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
library(stringr)
library(textstem)
library(tidyverse)
library(kableExtra)
theme_set(theme_bw())
library(ggrepel)
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00")
this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../../helpers.R")

# v1 <- read_csv("../../01_verbs/exploratory_all_data/data/processed.csv")
# v1["Category"] <- "Verbs"

v <- read_csv("../../01_concreteness/01_verbs/data/processed.csv")
v["Category"] <- "Verbs"
v["Experiment"] <- "Ex1a: Conc-Abs (Verbs)"
v["Conceptual"] <- "Conc-Abs"

n <- read_csv("../../01_concreteness/02_nouns/data/processed.csv")
n["Category"] <- "Nouns"
n["Experiment"] <- "Ex1b: Conc-Abs (Nouns)"
v["Conceptual"] <- "Conc-Abs"

a <- read_csv("../../01_concreteness/03_adjectives/data/processed.csv")
a["Category"] <- "Adjs"
a["Experiment"] <- "Ex1c: Conc-Abs (Adjs)"
a["Conceptual"] <- "Conc-Abs"

a2 <- read_csv("../../03_phys-soc/01_experiment/data/processed.csv")
a2["Category"] <- "Adjs"
a2["Experiment"] <- "Ex2b: Phys-Soc (Adjs)"
a2["Conceptual"] <- "Phys-Soc/Psych"

v2 <- read_csv("../../02_phys-psych/01_experiment/data/processed.csv")
v2["Category"] <- "Verbs"
v2["Experiment"] <- "Ex2a: Phys-Psych (Verbs)"
v2["Conceptual"] <- "Phys-Soc/Psych"


n2 <- read_csv("../../04_animacy/01_experiment/data/processed.csv")
n2["Category"] <- "Nouns"
n2["Experiment"] <- "Ex3: Animacy (Nouns)"
n2["Conceptual"] <- "Animacy"

s <- read_csv("../../05_syntactic/01_experiment/data/processed.csv")
s["Experiment"] <- "Ex4: Syntactic (N v. V)"
s["Conceptual"] <- "Syntactic"


d <- bind_rows(v,n,a,a2,v2,n2,s)
d <- d %>% 
  mutate(Task = ifelse(Task == "Valence", "Valence", "TruthCond"),
          Task = factor(Task, levels = c("TruthCond","Valence"))) 

# words <- unique(d[,c("Word","Experiment")])
# write.csv(words,"../data/total_words.csv")

```

```{r}
d <- d %>%
  group_by(Experiment,ID.true, Task, Word) %>%
  mutate(Repetition = row_number()) %>%
  ungroup()

table(d$Repetition)

sub <- d %>% 
  filter(Repetition >= 4)

table(sub$Experiment)
View(sub)

subb <- d %>% 
  filter(Experiment %in% c("Ex1b: Conc-Abs (Nouns)"))


table(subb$Word,subb$Repetition, subb$Task)

subbb <- subb %>% 
  filter(Word %in% c("despair","rust", "hug"))
ggplot(subbb, aes(Repetition, ReactionTime)) +
  stat_summary(fun = mean, geom = "line") +
  stat_summary(fun = mean, geom = "point") +
  facet_grid(Task ~ Word) +
  theme_minimal()


table(subbb$Word,subbb$Task,subbb$BlockOrder)

```


# Q1: ARE THERE ORDER EFFECTS?

```{r}

range(d$Repetition)

d.fil <- d %>% 
  filter(Repetition <= 3)
```


```{r}
ggplot(d.fil, aes(Repetition, ReactionTime)) +
  stat_summary(fun = mean, geom = "line") +
  stat_summary(fun = mean, geom = "point") +
  facet_grid(Task ~ Experiment) +
  theme_minimal()
```


```{r}

agr <- d.fil %>% 
  group_by(Experiment,Task,ID.true,Repetition) %>% 
  summarise(
    MeanLogRT = mean(log(ReactionTime), na.rm = TRUE),
    .groups = "drop"
  )

ggplot(agr, aes(x = Repetition, y = MeanLogRT, group = ID.true)) +
  geom_line(alpha = 0.3) +
  geom_point(alpha = 0.5, size = 1) +
  facet_grid(Task ~ Experiment) +
  theme_minimal() +
  labs(x = "Trial number", y = "Mean Log reaction time")


ggplot(agr, aes(x = Repetition, y = MeanLogRT)) +
  stat_summary(fun = mean, geom = "line", linewidth = 1) +
  stat_summary(fun = mean, geom = "point", size = 1.5) +
  facet_grid(Task ~ Experiment) +
  theme_minimal()
```


```{r}
d.fil %>%
  group_by(Experiment, Task, ID.true, Repetition) %>%
  summarise(MeanLogRT = mean(log(ReactionTime), na.rm = TRUE), .groups = "drop") %>%
  ggplot(aes(x = Repetition, y = MeanLogRT, group = ID.true)) +
  geom_line(alpha = 0.3) +
  geom_point(alpha = 0.5, size = 1) +
  facet_grid(Task ~ Experiment) +
  theme_minimal()
```

## Including Repetition makes for a more epxlanatiory model of reaction time (unsurprising)


Data: d.fil
Models:
m1: log(ReactionTime) ~ Task * Experiment + (1 + Task | ID.true) + (1 + Task | Word)
m2: log(ReactionTime) ~ Task * Experiment * Repetition + (1 + Task + Repetition | ID.true) + (1 + Repetition + Task | Word)
   npar   AIC   BIC logLik deviance  Chisq Df Pr(>Chisq)    
m1   21 56828 57019 -28393    56786                         
m2   63 52766 53339 -26320    52640 4145.6 42  < 2.2e-16 ***
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1


```{r}
names(d.fil)
d.fil$Task <- factor(d.fil$Task)
d.fil$Experiment <- factor(d.fil$Experiment)
d.fil$Repetition <- factor(d.fil$Repetition)

m1 <- lmer(
  log(ReactionTime) ~ Task * Experiment +
    (1 + Task | ID.true) +
    (1 + Task | Word),
  data = d.fil
)

m2 <- lmer(
  log(ReactionTime) ~ Task * Experiment * Repetition +
    (1 + Task + Repetition | ID.true) +
    (1 + Repetition + Task | Word),
  data = d.fil
)


anova(m1, m2)
```


## But Task is most important

Data: d.fil
Models:
m3: log(ReactionTime) ~ Experiment * Repetition + (1 + Repetition | ID.true) + (1 + Repetition | Word)
m2: log(ReactionTime) ~ Task * Experiment * Repetition + (1 + Task + Repetition | ID.true) + (1 + Repetition + Task | Word)
   npar   AIC   BIC logLik deviance  Chisq Df Pr(>Chisq)    
m3   34 60715 61024 -30323    60647                         
m2   63 52766 53339 -26320    52640 8006.4 29  < 2.2e-16 ***
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1


```{r}

m3 <- lmer(
  log(ReactionTime) ~ Experiment * Repetition +
    (1 + Repetition | ID.true) +
    (1 + Repetition | Word),
  data = d.fil
)

anova(m2,m3)
```




# Q2: Do negative ratings decrease over the course of the experiment

```{r}

View(d.fil)
val <- d.fil %>% 
  # filter((Task == "Valence")) %>% 
  # filter(Word %in% conc$Word) %>% 
  group_by(Experiment,Task,Word,Repetition) %>%
  mutate(Response.n = as.numeric(factor(Response, levels = c("negative", "positive"))) - 1) %>%  # Convert to numeric and subtract 1
  reframe(PropPositive = mean(Response.n),
          CILow = ci.low(Response.n), 
          CIHigh = ci.high(Response.n)) %>%
  mutate(YMin = PropPositive - CILow, 
         YMax = PropPositive + CIHigh)


dodge = position_dodge(.9)
ggplot(data=val, aes(x=reorder(Word,PropPositive),y=PropPositive,fill=Experiment)) +
  geom_bar(position=dodge,stat="identity",color = "black") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  # facet_wrap(~Task) +
  ylim(0,1) +
  labs(x = "Word") +
  theme(
    legend.position = "top",
    legend.direction = "horizontal", 
    axis.text.x = element_text(angle = 90, hjust  = 1))


```


```{r}
d.fil$Response.n <- ifelse(d.fil$Response == "positive", 1, 0)
table(d.fil$Task,d.fil*Repetition)

sum <- d.fil %>%
  group_by(Experiment, Repetition) %>%
  # mutate(Response.n = ifelse(Response == "positive", 1, 0) ) %>%
  # reframe(
  #   PropPositive = mean(Response.n),
  #   YMin = ci.low(Response.n),
  #   YMax = ci.high(Response.n)
  # )
  reframe(PropPositive = mean(Response.n),
          CILow = ci.low(Response.n), 
          CIHigh = ci.high(Response.n)) %>%
  mutate(YMin = PropPositive - CILow, 
         YMax = PropPositive + CIHigh)



ggplot(sum, aes(x = Repetition, y = PropPositive, color = factor(Experiment))) +
  geom_line(aes(group = Experiment), alpha = 0.7) +
  geom_point() +
  geom_errorbar(aes(ymin = YMin, ymax = YMax), width = 0.1) +
  stat_summary(
    aes(group = 1),
    fun = mean,
    geom = "line",
    linewidth = 1.5,
    color = "black"
  ) +
  labs(
    y = "Proportion Positive",
    x = "Repetition",
    color = "Experiment"
  ) +
  theme_minimal()
```

# Does PropPostive decrease over the course of Experiment
decreases but not significantly
```{r}
d.fil %>%
  group_by(Experiment,Repetition) %>%
  summarise(mean(Response.n))

model <- glmer(Response.n ~ Task*Repetition*Experiment +
               (1 + Task | Word) +
               (1 + Task | ID.true),
               family = binomial,
               data = d.fil)

summary(model)


model.scale <- glmer(Response.n ~ scale(Repetition)*Experiment +
               (1 | Word) +
               (1 | ID.true),
               family = binomial,
               data = d.fil)

summary(model.scale)
```



```{r}
ggplot(agr, aes(x = Repetition, y = MeanPropPositive)) +
  stat_summary(fun = mean, geom = "line", linewidth = 1) +
  stat_summary(fun = mean, geom = "point", size = 1.5) +
  facet_wrap(~ Experiment) +
  theme_minimal()

ggplot(agr, aes(x = Repetition, y = MeanLogRT, group = ID.true)) +
  geom_line(alpha = 0.3) +
  geom_point(alpha = 0.5, size = 1) +
  facet_grid(Task ~ Experiment) +
  theme_minimal() +
  labs(x = "Trial number", y = "Mean Log reaction time")


ggplot(agr, aes(x = Repetition, y = MeanLogRT)) +
  stat_summary(fun = mean, geom = "line", linewidth = 1) +
  stat_summary(fun = mean, geom = "point", size = 1.5) +
  facet_grid(Task ~ Experiment) +
  theme_minimal()

dodge = position_dodge(.9)
ggplot(data=val, aes(x=reorder(Word,PropPositive),y=PropPositive)) +
  geom_bar(position=dodge,stat="identity",color = "black") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  facet_wrap(~Experiment) +
  scale_fill_manual(values = valence_colors) +
  ylim(0,1) +
  labs(x = "Word") +
  theme(
    legend.position = "top",
    legend.direction = "horizontal", 
    axis.text.x = element_text(angle = 90, hjust  = 1))

```



