---
title: "Everything: Order Effects"
author: "author"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
library(stringr)
library(textstem)
library(tidyverse)
library(kableExtra)
theme_set(theme_bw())
library(ggrepel)
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00")
this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../../helpers.R")

# v1 <- read_csv("../../01_verbs/exploratory_all_data/data/processed.csv")
# v1["Category"] <- "Verbs"

v <- read_csv("../../01_concreteness/01_verbs/data/processed.csv")
v["Category"] <- "Verbs"
v["Experiment"] <- "Ex1a: Conc-Abs (Verbs)"
v["Conceptual"] <- "Conc-Abs"

n <- read_csv("../../01_concreteness/02_nouns/data/processed.csv")
n["Category"] <- "Nouns"
n["Experiment"] <- "Ex1b: Conc-Abs (Nouns)"
v["Conceptual"] <- "Conc-Abs"

a <- read_csv("../../01_concreteness/03_adjectives/data/processed.csv")
a["Category"] <- "Adjs"
a["Experiment"] <- "Ex1c: Conc-Abs (Adjs)"
a["Conceptual"] <- "Conc-Abs"

a2 <- read_csv("../../03_phys-soc/01_experiment/data/processed.csv")
a2["Category"] <- "Adjs"
a2["Experiment"] <- "Ex2b: Phys-Soc (Adjs)"
a2["Conceptual"] <- "Phys-Soc/Psych"

v2 <- read_csv("../../02_phys-psych/01_experiment/data/processed.csv")
v2["Category"] <- "Verbs"
v2["Experiment"] <- "Ex2a: Phys-Psych (Verbs)"
v2["Conceptual"] <- "Phys-Soc/Psych"


n2 <- read_csv("../../04_animacy/01_experiment/data/processed.csv")
n2["Category"] <- "Nouns"
n2["Experiment"] <- "Ex3: Animacy (Nouns)"
n2["Conceptual"] <- "Animacy"

s <- read_csv("../../05_syntactic/01_experiment/data/processed.csv")
s["Experiment"] <- "Ex4: Syntactic (N v. V)"
s["Conceptual"] <- "Syntactic"


d <- bind_rows(v,n,a,a2,v2,n2,s)
d <- d %>% 
  mutate(Task = ifelse(Task == "Valence", "Valence", "TruthCond"),
          Task = factor(Task, levels = c("TruthCond","Valence"))) 

# words <- unique(d[,c("Word","Experiment")])
# write.csv(words,"../data/total_words.csv")

```

# Create repetition variable
```{r}
d <- d %>%
  group_by(Experiment,ID.true, Task, Word) %>%
  mutate(Repetition = row_number()) %>%
  ungroup()
```

```{r}
table(d$Repetition)

sub <- d %>% 
  filter(Repetition >= 4)

table(sub$Experiment)
View(sub)

subb <- d %>% 
  filter(Experiment %in% c("Ex1b: Conc-Abs (Nouns)"))


table(subb$Word,subb$Repetition, subb$Task)

subbb <- subb %>% 
  filter(Word %in% c("despair","rust", "hug"))
ggplot(subbb, aes(Repetition, ReactionTime)) +
  stat_summary(fun = mean, geom = "line") +
  stat_summary(fun = mean, geom = "point") +
  facet_grid(Task ~ Word) +
  theme_minimal()


table(subbb$Word,subbb$Task,subbb$BlockOrder)

```


# Q1: ARE THERE ORDER EFFECTS?

```{r}

range(d$Repetition)

d.fil <- d %>% 
  filter(Repetition <= 3)
```


```{r}
ggplot(d.fil, aes(Repetition, ReactionTime)) +
  stat_summary(fun = mean, geom = "line") +
  stat_summary(fun = mean, geom = "point") +
  facet_grid(Task ~ Experiment) +
  theme_minimal()
```


```{r}

agr <- d.fil %>% 
  group_by(Experiment,Task,ID.true,Repetition) %>% 
  summarise(
    MeanLogRT = mean(log(ReactionTime), na.rm = TRUE),
    .groups = "drop"
  )

ggplot(agr, aes(x = Repetition, y = MeanLogRT, group = ID.true)) +
  geom_line(alpha = 0.3) +
  geom_point(alpha = 0.5, size = 1) +
  facet_grid(Task ~ Experiment) +
  theme_minimal() +
  labs(x = "Trial number", y = "Mean Log reaction time")


ggplot(agr, aes(x = Repetition, y = MeanLogRT)) +
  stat_summary(fun = mean, geom = "line", linewidth = 1) +
  stat_summary(fun = mean, geom = "point", size = 1.5) +
  facet_grid(Task ~ Experiment) +
  theme_minimal()
```


```{r}
d.fil %>%
  group_by(Experiment, Task, ID.true, Repetition) %>%
  summarise(MeanLogRT = mean(log(ReactionTime), na.rm = TRUE), .groups = "drop") %>%
  ggplot(aes(x = Repetition, y = MeanLogRT, group = ID.true)) +
  geom_line(alpha = 0.3) +
  geom_point(alpha = 0.5, size = 1) +
  facet_grid(Task ~ Experiment) +
  theme_minimal()
```

## Including Repetition makes for a more epxlanatiory model of reaction time (unsurprising)


Data: d.fil
Models:
m1: log(ReactionTime) ~ Task * Experiment + (1 + Task | ID.true) + (1 + Task | Word)
m2: log(ReactionTime) ~ Task * Experiment * Repetition + (1 + Task + Repetition | ID.true) + (1 + Repetition + Task | Word)
   npar   AIC   BIC logLik deviance  Chisq Df Pr(>Chisq)    
m1   21 56828 57019 -28393    56786                         
m2   63 52766 53339 -26320    52640 4145.6 42  < 2.2e-16 ***
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1


```{r}
names(d.fil)
d.fil$Task <- factor(d.fil$Task)
d.fil$Experiment <- factor(d.fil$Experiment)
d.fil$Repetition <- factor(d.fil$Repetition)

m1 <- lmer(
  log(ReactionTime) ~ Task * Experiment +
    (1 + Task | ID.true) +
    (1 + Task | Word),
  data = d.fil
)

m2 <- lmer(
  log(ReactionTime) ~ Task * Experiment * Repetition +
    (1 + Task + Repetition | ID.true) +
    (1 + Repetition + Task | Word),
  data = d.fil
)


anova(m1, m2)
```


## But Task is most important

Data: d.fil
Models:
m3: log(ReactionTime) ~ Experiment * Repetition + (1 + Repetition | ID.true) + (1 + Repetition | Word)
m2: log(ReactionTime) ~ Task * Experiment * Repetition + (1 + Task + Repetition | ID.true) + (1 + Repetition + Task | Word)
   npar   AIC   BIC logLik deviance  Chisq Df Pr(>Chisq)    
m3   34 60715 61024 -30323    60647                         
m2   63 52766 53339 -26320    52640 8006.4 29  < 2.2e-16 ***
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1


```{r}

m3 <- lmer(
  log(ReactionTime) ~ Experiment * Repetition +
    (1 + Repetition | ID.true) +
    (1 + Repetition | Word),
  data = d.fil
)

anova(m2,m3)
```




# Q2: Do negative ratings decrease over the course of the experiment

```{r}
val <- d.fil %>% 
  # filter((Task == "Valence")) %>% 
  # filter(Word %in% conc$Word) %>% 
  group_by(Experiment,Task,Word,Repetition) %>%
  mutate(Response.n = as.numeric(factor(Response, levels = c("negative", "positive"))) - 1) %>%  # Convert to numeric and subtract 1
  reframe(PropPositive = mean(Response.n),
          CILow = ci.low(Response.n), 
          CIHigh = ci.high(Response.n)) %>%
  mutate(YMin = PropPositive - CILow, 
         YMax = PropPositive + CIHigh)


dodge = position_dodge(.9)
ggplot(data=val, aes(x=reorder(Word,PropPositive),y=PropPositive,fill=Experiment)) +
  geom_bar(position=dodge,stat="identity",color = "black") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  # facet_wrap(~Task) +
  ylim(0,1) +
  labs(x = "Word") +
  theme(
    legend.position = "top",
    legend.direction = "horizontal", 
    axis.text.x = element_text(angle = 90, hjust  = 1))


```


```{r}
d.fil$Response.n <- ifelse(d.fil$Response == "positive", 1, 0)
table(d.fil$Task,d.fil*Repetition)

sum <- d.fil %>%
  group_by(Experiment, Repetition) %>%
  # mutate(Response.n = ifelse(Response == "positive", 1, 0) ) %>%
  # reframe(
  #   PropPositive = mean(Response.n),
  #   YMin = ci.low(Response.n),
  #   YMax = ci.high(Response.n)
  # )
  reframe(PropPositive = mean(Response.n),
          CILow = ci.low(Response.n), 
          CIHigh = ci.high(Response.n)) %>%
  mutate(YMin = PropPositive - CILow, 
         YMax = PropPositive + CIHigh)



ggplot(sum, aes(x = Repetition, y = PropPositive, color = factor(Experiment))) +
  geom_line(aes(group = Experiment), alpha = 0.7) +
  geom_point() +
  geom_errorbar(aes(ymin = YMin, ymax = YMax), width = 0.1) +
  stat_summary(
    aes(group = 1),
    fun = mean,
    geom = "line",
    linewidth = 1.5,
    color = "black"
  ) +
  labs(
    y = "Proportion Positive",
    x = "Repetition",
    color = "Experiment"
  ) +
  theme_minimal()
```

# Does PropPostive decrease over the course of Experiment
decreases but not significantly
```{r}
d.fil %>%
  group_by(Experiment,Repetition) %>%
  summarise(mean(Response.n))

model <- glmer(Response.n ~ Task*Repetition*Experiment +
               (1 + Task | Word) +
               (1 + Task | ID.true),
               family = binomial,
               data = d.fil)

summary(model)


model.scale <- glmer(Response.n ~ scale(Repetition)*Experiment +
               (1 | Word) +
               (1 | ID.true),
               family = binomial,
               data = d.fil)

summary(model.scale)
```



```{r}
ggplot(agr, aes(x = Repetition, y = MeanPropPositive)) +
  stat_summary(fun = mean, geom = "line", linewidth = 1) +
  stat_summary(fun = mean, geom = "point", size = 1.5) +
  facet_wrap(~ Experiment) +
  theme_minimal()

ggplot(agr, aes(x = Repetition, y = MeanLogRT, group = ID.true)) +
  geom_line(alpha = 0.3) +
  geom_point(alpha = 0.5, size = 1) +
  facet_grid(Task ~ Experiment) +
  theme_minimal() +
  labs(x = "Trial number", y = "Mean Log reaction time")


ggplot(agr, aes(x = Repetition, y = MeanLogRT)) +
  stat_summary(fun = mean, geom = "line", linewidth = 1) +
  stat_summary(fun = mean, geom = "point", size = 1.5) +
  facet_grid(Task ~ Experiment) +
  theme_minimal()

dodge = position_dodge(.9)
ggplot(data=val, aes(x=reorder(Word,PropPositive),y=PropPositive)) +
  geom_bar(position=dodge,stat="identity",color = "black") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  facet_wrap(~Experiment) +
  scale_fill_manual(values = valence_colors) +
  ylim(0,1) +
  labs(x = "Word") +
  theme(
    legend.position = "top",
    legend.direction = "horizontal", 
    axis.text.x = element_text(angle = 90, hjust  = 1))

```


# Looking only at the first observation of each word

## Subset the data

### 1. first only the task block shown first
```{r}
table(d$BlockOrder)

first.block.only <- d %>% 
  filter(
    # TruthCond First Order
    ((BlockOrder == "AV") & (Task == "TruthCond")) |
    ((BlockOrder == "CV") & (Task == "TruthCond")) |
    ((BlockOrder == "PV") & (Task == "TruthCond")) |
    ((BlockOrder == "SV") & (Task == "TruthCond")) |
      
    # Valence First Oder
    ((BlockOrder == "VA") & (Task == "Valence")) |
    ((BlockOrder == "VC") & (Task == "Valence")) |
    ((BlockOrder == "VP") & (Task == "Valence")) |
    ((BlockOrder == "VS") & (Task == "Valence"))
  )

# halves the data
nrow(first.block.only)/nrow(d)*100
```

### 2. Only first observation of a given word

```{r}
first.word.block.only <- first.block.only %>% 
  filter(Repetition == 1)

nrow(first.word.block.only)/nrow(d)*100

table(first.word.block.only$Experiment)
```

### 3. Look at the effects

Remove outliers

```{r}
# First remove inaccurate participants
length(unique(first.word.block.only$ID.true))
inacc.parts <- first.word.block.only %>% 
  group_by(Experiment,ID.true,Task,Category) %>% 
  summarise(MeanAccuracy = mean(Accuracy)) %>% 
  filter(MeanAccuracy < .75)
# How many participants have Accuracy < .75?
length(unique(inacc.parts$ID.true))
# Remove them
d.inaccurate.removed <- first.word.block.only %>% 
  anti_join(inacc.parts, by = "ID.true")
# Sanity check
length(unique(d.inaccurate.removed$ID.true))


# Second, remove all inaccurate trials
orig <- nrow(d.inaccurate.removed)
d.inaccurate.removed <- d.inaccurate.removed %>% 
  filter(Accuracy == 1)
nrow(d.inaccurate.removed)/orig*100


# Third, Remove subjects with ReactionTime higher than 3x IQR
summary(d.inaccurate.removed$LogReactionTime)
  #  Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  # 6.924   7.328   7.436   7.479   7.579  10.008 
range(d.inaccurate.removed$LogReactionTime)

hist(d.inaccurate.removed$LogReactionTime, breaks=100, col="lightblue", xlab="LogReactionTime (ms)",
        main="Histogram with Normal Curve")

quantile(d.inaccurate.removed$LogReactionTime, na.rm = TRUE)
IQR(d.inaccurate.removed$LogReactionTime, na.rm = TRUE)*3 # 0.7526289
cutoff.high <- quantile(d.inaccurate.removed$LogReactionTime, na.rm = TRUE)[4] + IQR(d.inaccurate.removed$LogReactionTime, na.rm = TRUE)*3 # 8.419261
cutoff.low <- quantile(d.inaccurate.removed$LogReactionTime, na.rm = TRUE)[2] - IQR(d.inaccurate.removed$LogReactionTime, na.rm = TRUE)*3# 6.5088838.419261


# remove subjects with ReactionTime higher than 3 x IQR
df.outliers.removed <- subset(d.inaccurate.removed, (d.inaccurate.removed$LogReactionTime > cutoff.low) & (d.inaccurate.removed$LogReactionTime < cutoff.high))

hist(df.outliers.removed$LogReactionTime, breaks=100, col="lightblue", xlab="LogReactionTime (ms)",
        main="Histogram with Normal Curve")

# write_csv(df.outliers.removed,"../data/categorization.csv")
nrow(df.outliers.removed)

length(unique(first.word.block.only$ID.true)) - length(unique(df.outliers.removed$ID.true))

# What percentage of data lost?
(1 - nrow(df.outliers.removed)/nrow(first.word.block.only)) *100

```



### Total RT with median and mode stats

```{r}
agr <- df.outliers.removed %>%
    group_by(Experiment,Task,Word) %>%
    summarize(MeanReactionTime = mean(ReactionTime), 
              CILow = ci.low(ReactionTime), 
              CIHigh = ci.high(ReactionTime)) %>%
    mutate(YMin = MeanReactionTime - CILow, 
           YMax = MeanReactionTime + CIHigh)

# Set dodge width to match violin grouping
dodge_width <- 0.9

ggplot(agr, aes(x = Experiment, y = MeanReactionTime, fill = Task)) + 
  geom_violin(trim = FALSE, alpha = 0.4, position = position_dodge(width = dodge_width)) +

  # Add mean point with matching dodge
  stat_summary(fun = mean,
               geom = "point",
               shape = 23,
               size = 2,
               position = position_dodge(width = dodge_width)) +
  
  stat_summary(fun = median,
                geom = "crossbar",
                width = 0.3, 
                linewidth = 0.2,
                position = position_dodge(width = dodge_width)) +
  
  labs(y = "Mean Reaction Time", x = "Experiment") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
  theme(
    legend.position = "top",
    legend.direction = "horizontal",
    axis.title.x=element_blank(),
    text = element_text(family = "Helvetica"),
    axis.title.y = element_text(size = 16),     # x-axis title
    axis.text.y  = element_text(size = 12),     # y-axis ticks
    axis.text.x  = element_text(size = 12),     # x-axis ticks
  )

```

```{r}
names(first.word.block.only)
m.first <- lmer(log(ReactionTime) ~ Task +
                (1 | ID.true) +
                (1 + Task | Word),
                data = df.outliers.removed)

summary(m.first)
```