---
title: 'Pilot 1: Training Items'
author: "morgan moyer"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
library(stringr)
library(textstem)
library(tidyverse)
theme_set(theme_bw())
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73")
this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../../../helpers.R")

# d <- read.csv("../data/processed.csv")
d.train <- read.csv("../data/processed_training.csv")
train.facts <- read.csv("../data/calibrators_with_factors.csv")
d.train <- d.train %>% 
  inner_join(.,train.facts,by="Word") %>% 
  rename(ConcValCombo = ConcValCombo_moderate) %>% 
  select(-c("Concreteness_moderate","Valence_moderate","X.y")) %>% 
  # Create an accuracy column
  mutate(Accuracy = mapply(function(value, pattern) {
  ifelse(grepl(value, pattern), 1, 0)
}, Value, ConcValCombo))

```

# Introduction

Look at training items

F key is always abstract or negative

```{r}
length(unique(d.train$ID.true))
table(d.train$Task, d.train$Key_value_F)
table(d.train$Task, d.train$Key_value_J)

table(d.train$Group, d.train$Key_value_F)
table(d.train$Group, d.train$Key_value_J)

# Create proportion column
table(d.train$ConcValCombo)
```




```{r}

names(d.train)
agr <- d.train %>% 
  filter(Task == "Semantic") %>% 
  mutate(Response.n = as.numeric(factor(Value, levels = c("abstract", "concrete"))) - 1) %>% 
  group_by(Word,ConcValCombo) %>%
  summarize(PropConcrete = mean(Response.n))
  # select(ID.true, Task,ConcValCombo, Word, WhoseList, Response)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=reorder(Word,PropConcrete),y=PropConcrete,fill=ConcValCombo)) +
  geom_bar(position=dodge,stat="identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


```{r}
agr <- d.train %>% 
  filter(Task == "Valence") %>% 
  mutate(Response.n = as.numeric(factor(Value, levels = c("negative", "positive"))) - 1) %>% 
  group_by(Word,ConcValCombo) %>%
  summarize(PropPositive = mean(Response.n))
  # select(ID.true, Task,ConcValCombo, Word, WhoseList, Response)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=reorder(Word,PropPositive),y=PropPositive,fill=ConcValCombo)) +
  geom_bar(position=dodge,stat="identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

# Accuracy

### Items without Neutral features

- only for ConcValCombo where accuracy is clear.
- Good news, participants are very accuracy on these items!
```{r}
agr <- d.train %>% 
  filter(ConcValCombo %in% c("abstract-negative","abstract-positive","concrete-negative","concrete-positive")) %>% 
  group_by(Task) %>% 
  summarize(MeanAccuracy = mean(Accuracy), 
          CILow = ci.low(Accuracy), 
          CIHigh = ci.high(Accuracy)) %>%
  mutate(YMin = MeanAccuracy - CILow, 
         YMax = MeanAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanAccuracy,fill=Task)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))

```

```{r,fig.width=10, fig.height=5}
agr <- d.train %>% 
  filter(ConcValCombo %in% c("abstract-negative","abstract-positive","concrete-negative","concrete-positive")) %>% 
  group_by(ID.true,Task) %>% 
  summarize(MeanAccuracy = mean(Accuracy), 
          CILow = ci.low(Accuracy), 
          CIHigh = ci.high(Accuracy)) %>%
  mutate(YMin = MeanAccuracy - CILow, 
         YMax = MeanAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=ID.true,y=MeanAccuracy,fill=Task)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

### All items with neutral features

```{r}
d.train$Response <- ifelse(d.train$Value %in% c("positive","concrete"), 1, 0)
```

```{r}
agr <- d.train %>% 
  filter(!ConcValCombo %in% c("abstract-negative","abstract-positive","concrete-negative","concrete-positive")) %>% 
  group_by(Task) %>% 
  summarize(MeanAccuracy = mean(Accuracy), 
          CILow = ci.low(Accuracy), 
          CIHigh = ci.high(Accuracy)) %>%
  mutate(YMin = MeanAccuracy - CILow, 
         YMax = MeanAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanAccuracy,fill=Task)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))

```


### Valance pos/neg with neutral conc
- No surprise that Concrete Task has 0 accuracy because 'neutral' category.
- good thing that Valence category is at ceiling for accuracy
```{r}

agr <- d.train %>% 
  filter(ConcValCombo %in% c("neutral-positive","neutral-negative")) %>% 
  group_by(Task) %>% 
  summarize(MeanAccuracy = mean(Accuracy), 
          CILow = ci.low(Accuracy), 
          CIHigh = ci.high(Accuracy)) %>%
  mutate(YMin = MeanAccuracy - CILow, 
         YMax = MeanAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanAccuracy,fill=Task)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))

```


### Concreteness abs/conc with neutral valance
- again, good news that accuracy here is at ceiling
```{r}
agr <- d.train %>% 
  filter(ConcValCombo %in% c("abstract-neutral","concrete-neutral")) %>% 
  group_by(Task) %>% 
  summarize(MeanAccuracy = mean(Accuracy), 
          CILow = ci.low(Accuracy), 
          CIHigh = ci.high(Accuracy)) %>%
  mutate(YMin = MeanAccuracy - CILow, 
         YMax = MeanAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanAccuracy,fill=Task)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))
```


```{r}
agr <- d.train %>% 
  # filter(Task == "Valence") %>% 
  filter(ConcValCombo %in% c("abstract-neutral","concrete-neutral","neutral-positive","neutral-negative")) %>% 
  group_by(Task) %>%
  summarize(MeanPosConc = mean(Response), 
          CILow = ci.low(Response), 
          CIHigh = ci.high(Response)) %>%
  mutate(YMin = MeanPosConc - CILow, 
         YMax = MeanPosConc + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanPosConc,fill=Task)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))

```



## Reaction Time

```{r}

agr <- d.train %>% 
  group_by(Task) %>% 
  summarize(MeanReactionTime = mean(ReactionTime), 
          CILow = ci.low(ReactionTime), 
          CIHigh = ci.high(ReactionTime)) %>%
  mutate(YMin = MeanReactionTime - CILow, 
         YMax = MeanReactionTime + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanReactionTime,fill=Task)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))

```



## RT by Accuracy

```{r}
ggplot(d.train, aes(x = Accuracy, y = LogReactionTime, fill = Task)) +
  geom_violin(alpha = 0.7) + # Violin plot
  geom_jitter( color = "black", size = 1.5, alpha = 0.5) + # Add jittered points
  labs(title = "Reaction Time by Accuracy",
       x = "Accuracy",
       y = "Reaction Time (ms)")
  # theme_minimal() +
  # theme(legend.position = "none") # Remove legend
```


Plot as a function of trial order

```{r}

agr <- d.train %>% 
  group_by(Task,TrialNumber) %>% 
  summarize(MeanReactionTime = mean(ReactionTime), 
          CILow = ci.low(ReactionTime), 
          CIHigh = ci.high(ReactionTime)) %>%
  mutate(YMin = MeanReactionTime - CILow, 
         YMax = MeanReactionTime + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=TrialNumber,y=MeanReactionTime,fill=Task)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))

```
