---
title: "Pilot 4: troubleshoot concvalcombo"
author: "morgan moyer"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
library(stringr)
library(textstem)
library(tidyverse)
library(kableExtra)
theme_set(theme_bw())
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73")
this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../../../helpers.R")

d <- read.csv("../data/processed.csv")
c <- read.csv("../data/verbs_corpus.csv")

facts <- read.csv("../data/pilot4_words.csv")[,c("Word","ConcValStrict")]
facts_exp <- read.csv("../data/pilot4_valance.csv")[,c("Word","ConcValStrict")] %>% distinct()

names(c)

length(unique(d$Word))

```

# First: Are the two factors files the same? (did I save the files at different times during categorization?)
yes it seems that they are 
```{r}
# Perform a left join to compare values
comparison <- facts %>%
  left_join(facts_exp, by = "Word", suffix = c("_facts", "_facts_exp")) %>%
  mutate(
    Match = ifelse(ConcValStrict_facts == ConcValStrict_facts_exp, "Match", "No Match")
  )

# Separate the matches and mismatches
matches <- comparison %>% filter(Match == "Match")
mismatches <- comparison %>% filter(Match == "No Match")

# View results
print(matches)
print(mismatches)
```


```{r}
dc <- d %>% 
  inner_join(c,by="Word")
length(unique(dc$Word))

not.there <- d %>% 
  anti_join(c,by="Word")
length(unique(not.there$Word))


# these seem reasonable?
not.there %>% 
  # group_by(Word, ConcValCombo) %>%
  group_by(ConcValCombo) %>%
  summarise(Word_List = paste(unique(Word), collapse = ", ")) %>%
  pivot_wider(names_from = ConcValCombo, values_from = Word_List) %>%
  knitr::kable() %>% 
  kable_styling(full_width = TRUE, position = "center", bootstrap_options = c("striped", "hover"))

# rename for later mergiing
not.there["ConcValFinal"] <- not.there["ConcValCombo"]


dc %>% 
  group_by(ConcValCombo_moderate) %>%
  summarise(Word_List = paste(unique(Word), collapse = ", ")) %>%
  pivot_wider(names_from = ConcValCombo_moderate, values_from = Word_List) %>%
  knitr::kable() %>% 
  kable_styling(full_width = TRUE, position = "center", bootstrap_options = c("striped", "hover"))

overlap <- dc %>% 
    filter(!grepl("neutral", ConcValCombo_moderate))
length(unique(overlap$Word))


rest <- dc %>% 
    filter(grepl("neutral", ConcValCombo_moderate))
length(unique(rest$Word))


```



```{r}

table(d$Key_value_F,d$Group)
table(d$Key_value_J,d$Group)

agr <- d %>% 
  filter(Task == "Concrete") %>% 
  filter(Word %in% c("fall","hurl","qualify")) %>% 
  mutate(Response.n = as.numeric(factor(Response, levels = c("abstract", "concrete"))) - 1) %>% 
  group_by(Word,ConcValCombo) %>%
  summarize(PropConcrete = mean(Response.n))
  # select(ID.true, Task,ConcValCombo, Word, WhoseList, Response)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=reorder(Word,PropConcrete),y=PropConcrete,fill=ConcValCombo)) +
  geom_bar(position=dodge,stat="identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")
```


# PropPositive and PropConcrete

Look at PropPositive and PropConcrete rather than Accuracy

## Valance
- Basically nothing is going wrong here it seems
- No differences between Pilot and Corpus Categorization

```{r,fig.width=10, fig.height=5}
val <- overlap %>% 
  filter(Task == "Valence") %>% 
  # filter(Word %in% conc$Word) %>% 
  group_by(Word,ConcValCombo) %>%
  mutate(Response.n = as.numeric(factor(Response, levels = c("negative", "positive"))) - 1) %>%  # Convert to numeric and subtract 1
  summarize(PropPositive = mean(Response.n))
  # filter(PropPositive > .1 | PropPositive < .9)

dodge = position_dodge(.9)
ggplot(data=val, aes(x=reorder(Word,PropPositive),y=PropPositive,fill=ConcValCombo)) +
  geom_bar(position=dodge,stat="identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")
```

```{r,fig.width=10, fig.height=5}
val <- overlap %>% 
  filter(Task == "Valence") %>% 
  # filter(Word %in% conc$Word) %>% 
  group_by(Word,ConcValCombo_moderate) %>%
  mutate(Response.n = as.numeric(factor(Response, levels = c("negative", "positive"))) - 1) %>%  # Convert to numeric and subtract 1
  summarize(PropPositive = mean(Response.n))
  # filter(PropPositive > .1 | PropPositive < .9)

dodge = position_dodge(.9)
ggplot(data=val, aes(x=reorder(Word,PropPositive),y=PropPositive,fill=ConcValCombo_moderate)) +
  geom_bar(position=dodge,stat="identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")
```

## Concrete

### Coding from pilot results 
- there must be an error going on here
```{r,fig.width=10, fig.height=5}
conc <- overlap %>% 
  filter(Task == "Concrete") %>% 
  # filter(Word %in% conc$Word) %>% 
  group_by(Word,ConcValCombo) %>%
  mutate(Response.n = as.numeric(factor(Response, levels = c("abstract", "concrete"))) - 1) %>%  # Convert to numeric and subtract 1
  summarize(PropConcrete = mean(Response.n))
  # filter(PropPositive > .1 | PropPositive < .9)

dodge = position_dodge(.9)
ggplot(data=conc, aes(x=reorder(Word,PropConcrete),y=PropConcrete,fill=ConcValCombo)) +
  geom_bar(position=dodge,stat="identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")
```

### Coding from the corpus
- this one seems to be categorizing correctly

```{r,fig.width=10, fig.height=5}
conc <- overlap %>% 
  filter(Task == "Concrete") %>% 
  # filter(Word %in% conc$Word) %>% 
  group_by(Word,ConcValCombo_moderate) %>%
  mutate(Response.n = as.numeric(factor(Response, levels = c("abstract", "concrete"))) - 1) %>%  # Convert to numeric and subtract 1
  summarize(PropConcrete = mean(Response.n))
  # filter(PropPositive > .1 | PropPositive < .9)

dodge = position_dodge(.9)
ggplot(data=conc, aes(x=reorder(Word,PropConcrete),y=PropConcrete,fill=ConcValCombo_moderate)) +
  geom_bar(position=dodge,stat="identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")
```

```{r}
conc.d <- conc %>% 
  inner_join(d,by="Word")

```


### Now take a look at accuracy and compare how it differs with the two categorizations
- Accuracy is much lower using the results from the pilot
- Either there's lots of variability in participant responses or I've made a coding error 
- Conclusion: Recode using the corpus categorization

```{r,fig.width=10, fig.height=5}
conc.d$AccuracyTestCorpus <- mapply(function(response, pattern) {
  ifelse(grepl(response, pattern), 1, 0)
}, conc.d$Response, conc.d$ConcValCombo_moderate)

agr <- conc.d %>%
  group_by(Word,ConcValCombo_moderate) %>% 
  mutate(MeanAccuracy = mean(AccuracyTestCorpus), 
          CILow = ci.low(AccuracyTestCorpus), 
          CIHigh = ci.high(AccuracyTestCorpus)) %>%
  mutate(YMin = MeanAccuracy - CILow, 
         YMax = MeanAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Word,y=MeanAccuracy,fill=ConcValCombo_moderate)) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))

```


```{r,fig.width=10, fig.height=5}
conc.d$AccuracyTestPilot <- mapply(function(response, pattern) {
  ifelse(grepl(response, pattern), 1, 0)
}, conc.d$Response, conc.d$ConcValCombo)

agr <- conc.d %>%
  group_by(Word,ConcValCombo) %>% 
  mutate(MeanAccuracy = mean(AccuracyTestPilot), 
          CILow = ci.low(AccuracyTestPilot), 
          CIHigh = ci.high(AccuracyTestPilot)) %>%
  mutate(YMin = MeanAccuracy - CILow, 
         YMax = MeanAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Word,y=MeanAccuracy,fill=ConcValCombo)) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))

```

#### Recode

```{r}
overlap %>% 
  group_by(ConcValCombo) %>%
  summarise(Word_List = paste(unique(Word), collapse = ", ")) %>%
  pivot_wider(names_from = ConcValCombo, values_from = Word_List) %>%
  knitr::kable() %>% 
  kable_styling(full_width = TRUE, position = "center", bootstrap_options = c("striped", "hover"))

overlap %>% 
  group_by(ConcValCombo_moderate) %>%
  summarise(Word_List = paste(unique(Word), collapse = ", ")) %>%
  pivot_wider(names_from = ConcValCombo_moderate, values_from = Word_List) %>%
  knitr::kable() %>% 
  kable_styling(full_width = TRUE, position = "center", bootstrap_options = c("striped", "hover"))
```

Filter rows where ConcValCombo and ConcValCombo_moderate are NOT the same

```{r}

# Filter rows where ConcValCombo and ConcValCombo_moderate are not the same
rows_different <- overlap %>%
  filter(ConcValCombo != ConcValCombo_moderate)

length(unique(overlap$Word))
print(unique(overlap$Word))
# View or inspect the resulting rows
length(unique(rows_different$Word))

table(rows_different$Word,rows_different$ConcValCombo_moderate)


# Create ConcValFinal based on Corpus
rows_different <- rows_different %>% 
  mutate(ConcValFinal = ConcValCombo_moderate)
  
```


Filter rows where ConcValCombo and ConcValCombo_moderate ARE the same

```{r}

rows_same <- overlap %>%
  filter(ConcValCombo == ConcValCombo_moderate)  

print(unique(rows_same$Word))
# Sanity check
table(rows_same$Word,rows_same$ConcValCombo)
table(rows_same$Word,rows_same$ConcValCombo_moderate)
# Creat ConValFinal Column based on Pilot or Corpus
rows_same <- rows_same %>% 
  mutate(ConcValFinal = ConcValCombo)

```



# neutral Words
- i think we can go with ConcValCombo from Pilot


## Coding from pilot data
Actually here it seems to be working fine?
- so cases where empirically 
```{r,fig.width=10, fig.height=5}
conc <- rest %>% 
  filter(Task == "Concrete") %>% 
  # filter(Word %in% conc$Word) %>% 
  group_by(Word,ConcValCombo) %>%
  mutate(Response.n = as.numeric(factor(Response, levels = c("abstract", "concrete"))) - 1) %>%  # Convert to numeric and subtract 1
  summarize(PropConcrete = mean(Response.n))
  # filter(PropPositive > .1 | PropPositive < .9)

dodge = position_dodge(.9)
ggplot(data=conc, aes(x=reorder(Word,PropConcrete),y=PropConcrete,fill=ConcValCombo)) +
  geom_bar(position=dodge,stat="identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")
```


## Coding from Corpus
```{r,fig.width=10, fig.height=5}
conc <- rest %>% 
  filter(Task == "Concrete") %>% 
  # filter(Word %in% conc$Word) %>% 
  group_by(Word,ConcValCombo_moderate) %>%
  mutate(Response.n = as.numeric(factor(Response, levels = c("abstract", "concrete"))) - 1) %>%  # Convert to numeric and subtract 1
  summarize(PropConcrete = mean(Response.n))
  # filter(PropPositive > .1 | PropPositive < .9)

dodge = position_dodge(.9)
ggplot(data=conc, aes(x=reorder(Word,PropConcrete),y=PropConcrete,fill=ConcValCombo_moderate)) +
  geom_bar(position=dodge,stat="identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")
```


```{r}
rest <- rest %>% 
  mutate(ConcValFinal = ConcValCombo)
```


# Trying now to look at accuracy

```{r, eval=FALSE, echo=FALSE}
dc$AccuracyFinal <- mapply(function(response, pattern) {
  ifelse(grepl(response, pattern), 1, 0)
}, d$Response, d$ConcValComboFinal)

```


## Overall Accuracy

```{r,fig.width=10, fig.height=5}
agr <- d %>% 
  group_by(Task) %>% 
  reframe(MeanAccuracy = mean(Accuracy), 
          CILow = ci.low(Accuracy), 
          CIHigh = ci.high(Accuracy)) %>%
  mutate(YMin = MeanAccuracy - CILow, 
         YMax = MeanAccuracy + CIHigh)
# View(agr)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanAccuracy)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))

  # theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  # guides(fill = "none")

```

## Mean Accuracy by Word / Task
```{r,fig.width=10, fig.height=15}
agr <- d %>%
  # filter(PennElementType == "Selector") %>% 
  # select(ID.true,Word,Accuracy) %>% 
  group_by(Task,Word) %>% 
  mutate(MeanAccuracy = mean(Accuracy), 
          CILow = ci.low(Accuracy), 
          CIHigh = ci.high(Accuracy)) %>%
  mutate(YMin = MeanAccuracy - CILow, 
         YMax = MeanAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanAccuracy,fill=Task)) +
  geom_bar(position=dodge,stat="identity") +
  facet_wrap(~Word,ncol=10) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  # theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  guides(fill = "none")

# View(d[(d$ID.true == c("56cc78e3ccc0e20006b82a7d")) & (d$Word == c("envy")),])
```

# combine all the fixed outputs

```{r}
names(rows_same)
names(rows_different)
names(not.there)
names(rest)

# List of all data frames to combine
dfs <- list(rows_same, rows_different, not.there, rest)

# Find shared column names
shared_columns <- Reduce(intersect, lapply(dfs, colnames))

# Select shared columns from each data frame and combine them
combined_df <- bind_rows(lapply(dfs, function(df) select(df, all_of(shared_columns))))

# Amazing!
length(unique(combined_df$Word))

names(combined_df)

grpd <- combined_df %>% 
  group_by(Word,ConcValFinal) %>% 
  unique()

View(grpd)  
table(grpd$ConcValFinal)

```

```{r,fig.width=10, fig.height=5}
conc <- combined_df %>% 
  filter(Task == "Concrete") %>% 
  # filter(Word %in% conc$Word) %>% 
  group_by(Word,ConcValFinal) %>%
  mutate(Response.n = as.numeric(factor(Response, levels = c("abstract", "concrete"))) - 1) %>%  # Convert to numeric and subtract 1
  summarize(PropConcrete = mean(Response.n))
  # filter(PropPositive > .1 | PropPositive < .9)

dodge = position_dodge(.9)
ggplot(data=conc, aes(x=reorder(Word,PropConcrete),y=PropConcrete,fill=ConcValFinal)) +
  geom_bar(position=dodge,stat="identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")
```

```{r,fig.width=10, fig.height=5}
val <- combined_df %>% 
  filter(Task == "Valence") %>% 
  # filter(Word %in% conc$Word) %>% 
  group_by(Word,ConcValFinal) %>%
  mutate(Response.n = as.numeric(factor(Response, levels = c("negative", "positive"))) - 1) %>%  # Convert to numeric and subtract 1
  summarize(PropPositive = mean(Response.n))
  # filter(PropPositive > .1 | PropPositive < .9)

dodge = position_dodge(.9)
ggplot(data=val, aes(x=reorder(Word,PropPositive),y=PropPositive,fill=ConcValFinal)) +
  geom_bar(position=dodge,stat="identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  # guides(fill = "none")
```

```{r,fig.width=10, fig.height=5}
combined_df$AccuracyCorrected <- mapply(function(response, pattern) {
  ifelse(grepl(response, pattern), 1, 0)
}, combined_df$Response, combined_df$ConcValFinal)

agr <- combined_df %>%
  group_by(Word,ConcValFinal) %>% 
  mutate(MeanCorrectedAccuracy = mean(AccuracyCorrected), 
          CILow = ci.low(AccuracyCorrected), 
          CIHigh = ci.high(AccuracyCorrected)) %>%
  mutate(YMin = MeanCorrectedAccuracy - CILow, 
         YMax = MeanCorrectedAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Word,y=MeanCorrectedAccuracy,fill=ConcValFinal)) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))

```
# Save to .csv 
```{r}
# write.csv(combined_df,"../data/corrected.csv")
```

