---
title: 'Pilot 1: troubleshooting with training and choice lables'
author: "morgan moyer"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
library(stringr)
library(textstem)
library(tidyverse)
theme_set(theme_bw())
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73")
this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../../../helpers.R")

d <- read.csv("../data/processed.csv")
```


```{r}
dconc <- d %>% 
  filter(Task == "Semantic")

table(dconc$Value,dconc$Key_value_F)
View(d)
```


```{r}
agr <- d %>% 
  # filter(Version == "Pilot1") %>% 
  filter(Task == "Semantic") %>% 
  filter(Word %in% c("fall","hurl","qualify")) %>% 
  mutate(Response.n = as.numeric(factor(Response, levels = c("abstract", "concrete"))) - 1) %>% 
  group_by(Word,ConcValCombo) %>%
  summarize(PropConcrete = mean(Response.n))
  # select(ID.true, Task,ConcValCombo, Word, WhoseList, Response)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=reorder(Word,PropConcrete),y=PropConcrete,fill=ConcValCombo)) +
  geom_bar(position=dodge,stat="identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


# Introduction

What's going on with the low accuracy on Concrete Trials?


TL;DR:
- basically there's a coding error, and people actually ARE accurate.



# Look at the test items where there was/wasn't a switch in the lables
#Find participants in test items where F = abstract/negative and J != concrete/positive

```{r}

table(d$Key_value_J,d$Task,d$Group)
table(d$Comment,d$Task)

test.switch <- d %>% 
  # Since training was always F = negative/abstract, switch is the opposite
  filter((!Key_value_J %in% c("positive","concrete"))
           # (PennElementType == "Selector")
         ) 
switch.IDs <- test.switch$ID.true

# how many participants have the switch?
length(unique(test.switch$ID.true))

nrow(test.switch)
nrow(d)

```

### How does accuracy and RT change in these cases?
Interestingly, Concrete accuracy is higher than for valance?
```{r}
agr <- d %>% 
  group_by(Task) %>% 
  summarize(MeanAccuracy = mean(Accuracy), 
          CILow = ci.low(Accuracy), 
          CIHigh = ci.high(Accuracy)) %>%
  mutate(YMin = MeanAccuracy - CILow, 
         YMax = MeanAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanAccuracy,fill=Task)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))

```


```{r,fig.width=10, fig.height=15}
agr <- d %>% 
  group_by(Task,Word) %>% 
  summarize(MeanAccuracy = mean(Accuracy), 
          CILow = ci.low(Accuracy), 
          CIHigh = ci.high(Accuracy)) %>%
  mutate(YMin = MeanAccuracy - CILow, 
         YMax = MeanAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Task,y=MeanAccuracy,fill=Task)) +
  geom_bar(position=dodge,stat="identity") + 
  facet_wrap(~Word,ncol=5) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9))

```




## In the No Switch trials

```{r}

test.no.switch.conc <- test.no.switch %>% 
  filter(Task == "Concrete") %>% 
  mutate(Response.n = ifelse(Response == "concrete", 1, 0) )

test.no.switch.conc$Response.n = as.numeric(test.no.switch.conc$Response.n)

```


```{r,fig.width=10, fig.height=5}
agr <- test.no.switch.conc %>% 
  group_by(Word) %>% 
  summarize(PropConcrete = mean(Response.n),
          CILow = ci.low(Response.n),
          CIHigh = ci.high(Response.n)) %>%
  mutate(YMin = PropConcrete - CILow,
         YMax = PropConcrete + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Word,y=PropConcrete,fill=Word)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

## In the Switch trials

```{r}

test.switch.conc <- test.switch %>% 
  filter(Task == "Concrete") %>% 
  mutate(Response.n = ifelse(Response == "concrete", 1, 0) )

test.switch.conc$Response.n = as.numeric(test.switch.conc$Response.n)

```


```{r,fig.width=10, fig.height=5}
agr <- test.switch.conc %>% 
  group_by(Word) %>% 
  summarize(PropConcrete = mean(Response.n),
          CILow = ci.low(Response.n),
          CIHigh = ci.high(Response.n)) %>%
  mutate(YMin = PropConcrete - CILow,
         YMax = PropConcrete + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Word,y=PropConcrete,fill=Word)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


# Add a switch column

```{r}
# Add Task column
d$Switch <- ifelse(d$Key_value_F %in% c("concrete","positive"), "Switch","NoSwitch")
d$Response.n = as.numeric(d$Response)

```


What we can see from the following graph, is that the key labels are clearly inverted....but only for the concreteness task. responses are more or less in complementary distributions


```{r,fig.width=10, fig.height=5}
agr <- d %>% 
  filter(Task == "Concrete") %>% 
  mutate(Response.n = ifelse(Response == "concrete", 1, 0),
         Response.n = as.numeric(Response.n)) %>% 
  group_by(Switch,Word) %>% 
  summarize(PropConcrete = mean(Response.n),
          CILow = ci.low(Response.n),
          CIHigh = ci.high(Response.n)) %>%
  mutate(YMin = PropConcrete - CILow,
         YMax = PropConcrete + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Word,y=PropConcrete,fill=Switch)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


So in the NoSwitch conditions there's mislableing.
```{r,fig.width=10, fig.height=5}
agr <- d %>% 
  filter(Task == "Concrete") %>% 
  group_by(Switch,Word) %>% 
  summarize(MeanAccuracy = mean(Accuracy),
          CILow = ci.low(Accuracy),
          CIHigh = ci.high(Accuracy)) %>%
  mutate(YMin = MeanAccuracy - CILow,
         YMax = MeanAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Word,y=MeanAccuracy,fill=Switch)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


## Valence task

Actually Switching does seem to decrease accuracy
```{r,fig.width=10, fig.height=5}
agr <- d %>% 
  filter(Task == "Valence") %>% 
  mutate(Response.n = ifelse(Response == "positive", 1, 0),
         Response.n = as.numeric(Response.n)) %>% 
  group_by(Switch,Word) %>% 
  summarize(PropPositive = mean(Response.n),
          CILow = ci.low(Response.n),
          CIHigh = ci.high(Response.n)) %>%
  mutate(YMin = PropPositive - CILow,
         YMax = PropPositive + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Word,y=PropPositive,fill=Switch)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


```{r,fig.width=10, fig.height=5}
agr <- d %>% 
  filter(Task == "Valence") %>% 
  group_by(Switch,Word) %>% 
  summarize(MeanAccuracy = mean(Accuracy),
          CILow = ci.low(Accuracy),
          CIHigh = ci.high(Accuracy)) %>%
  mutate(YMin = MeanAccuracy - CILow,
         YMax = MeanAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Word,y=MeanAccuracy,fill=Switch)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

Corrective column and save to CSV

```{r, eval=FALSE,echo=FALSE}
d <- d %>%
  mutate(CorrectedResponse = case_when(
    Switch == "NoSwitch" & Task == "Concrete" & Response == "concrete" ~ "abstract",
    Switch == "NoSwitch" & Task == "Concrete" & Response == "abstract" ~ "concrete",
    TRUE ~ Response  # For all other cases, keep the value of Response
  ))

d$CorrectedAccuracy <- mapply(function(correctedresponse, pattern) {
  ifelse(grepl(correctedresponse, pattern), 1, 0)
}, d$CorrectedResponse, d$ConcValCombo)
```

Save to .csv
```{r}
# write.csv(d,"../data/corrected.csv")
```

This graph should look different:

```{r}
agr <- d %>% 
  filter(Task == "Concrete") %>% 
  group_by(Switch,Word) %>% 
  summarize(MeanCorrectedAccuracy = mean(CorrectedAccuracy),
          CILow = ci.low(CorrectedAccuracy),
          CIHigh = ci.high(CorrectedAccuracy)) %>%
  mutate(YMin = MeanCorrectedAccuracy - CILow,
         YMax = MeanCorrectedAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Word,y=MeanCorrectedAccuracy,fill=Switch)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

This graph should look the same.
```{r}
agr <- d %>% 
  filter(Task == "Valence") %>% 
  group_by(Switch,Word) %>% 
  summarize(MeanCorrectedAccuracy = mean(CorrectedAccuracy),
          CILow = ci.low(CorrectedAccuracy),
          CIHigh = ci.high(CorrectedAccuracy)) %>%
  mutate(YMin = MeanCorrectedAccuracy - CILow,
         YMax = MeanCorrectedAccuracy + CIHigh)

dodge = position_dodge(.9)
ggplot(data=agr, aes(x=Word,y=MeanCorrectedAccuracy,fill=Switch)) +
  geom_bar(position=dodge,stat="identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
